---
title: "Performance Comparison"
author: "Alessandra Pescina"
date: "2024-12-16"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, results='hide'}


knitr::opts_chunk$set(
  echo = FALSE,           
  warning = FALSE,      
  message = FALSE,       
  fig.align = "center",  
  fig.width = 12,        
  fig.height = 8,        
  out.width = "100%"     
)



```



```{r}
library(fs)
library(parallel)
library(ggplot2)
library(dplyr)
library(tidyr)
library(patchwork)
library(here)
library(kableExtra)
library(plotly)
```


```{r}
setwd(here())
path <- "./wrapper_MM/saved_performance_500/"
files <- list.files(path, pattern = "\\.RData$", full.names = TRUE)
lapply(files, load, .GlobalEnv)

combined_cov500 <- combined_cov 
remove(combined_cov)

res_cov_ic500 <- res_cov_ic
remove(res_cov_ic)

ct_all_schemes500 <- ct_all_schemes
remove(ct_all_schemes)

mean_estimates_lfe500 <- mean_estimates_lfe
remove(mean_estimates_lfe)

res_bias500 <- res_bias
remove(res_bias)

res_bias_lfe500 <- res_bias_lfe
remove(res_bias_lfe)

plots_errorI500 <- plots_errorI
remove(plots_errorI)

plots_power500 <- plots_power 
remove(plots_power)
```

```{r, results='hide'}

setwd(here())
path <- "./wrapper_MM/saved_performance_2K/"
files <- list.files(path, pattern = "\\.RData$", full.names = TRUE)
lapply(files, load, .GlobalEnv)

combined_cov2K <- combined_cov 
remove(combined_cov)

res_cov_ic2K <- res_cov_ic
remove(res_cov_ic)

ct_all_schemes2K <- ct_all_schemes
remove(ct_all_schemes)

mean_estimates_lfe2K <- mean_estimates_lfe
remove(mean_estimates_lfe)

res_bias2K <- res_bias
remove(res_bias)

res_bias_lfe2K <- res_bias_lfe
remove(res_bias_lfe)

plots_errorI2K<- plots_errorI
remove(plots_errorI)

plots_power2K <- plots_power 
remove(plots_power)

```

```{r, results='hide'}

setwd(here())
path <- "./wrapper_MM/saved_performance_5K/"
files <- list.files(path, pattern = "\\.RData$", full.names = TRUE)
lapply(files, load, .GlobalEnv)

combined_cov5K <- combined_cov 
remove(combined_cov)

res_cov_ic5K <- res_cov_ic
remove(res_cov_ic)

ct_all_schemes5K <- ct_all_schemes
remove(ct_all_schemes)

mean_estimates_lfe5K <- mean_estimates_lfe
remove(mean_estimates_lfe)

res_bias5K <- res_bias
remove(res_bias)

res_bias_lfe5K <- res_bias_lfe
remove(res_bias_lfe)

plots_errorI5K <- plots_errorI
remove(plots_errorI)

plots_power5K <- plots_power 
remove(plots_power)

```

```{r}
setwd(here())
path <- "./wrapper_MM/saved_performance_10K/"
files <- list.files(path, pattern = "\\.RData$", full.names = TRUE)
lapply(files, load, .GlobalEnv)

combined_cov10K <- combined_cov 
remove(combined_cov)

res_cov_ic10K <- res_cov_ic
remove(res_cov_ic)

ct_all_schemes10K <- ct_all_schemes
remove(ct_all_schemes)

mean_estimates_lfe10K <- mean_estimates_lfe
remove(mean_estimates_lfe)

res_bias10K <- res_bias
remove(res_bias)

res_bias_lfe10K <- res_bias_lfe
remove(res_bias_lfe)

plots_errorI10K <- plots_errorI
remove(plots_errorI)

plots_power10K <- plots_power 
remove(plots_power)



```

```{r}
model_dir <- here() 
setwd(model_dir)
model_dir <- paste0("wrapper_MM/plots")
dir.create(model_dir, showWarnings = FALSE, recursive= T)
```

### Absolute Bias of covariates effect 


Absolute bias of covariates effect varying observational scheme for a chosen sample size
```{r}

p1 <- res_bias500[[1]]
p2 <- res_bias500[[2]]
p3 <- res_bias500[[3]]
p4 <- res_bias500[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df1 <- rbind(p1,p2,p3,p4)
df1$size <- "500 individuals"

p1 <- res_bias2K[[1]]
p2 <- res_bias2K[[2]]
p3 <- res_bias2K[[3]]
p4 <- res_bias2K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df2 <- rbind(p1,p2,p3,p4)
df2$size <- "2000 individuals"


p1 <- res_bias5K[[1]]
p2 <- res_bias5K[[2]]
p3 <- res_bias5K[[3]]
p4 <- res_bias5K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df3 <- rbind(p1,p2,p3,p4)
df3$size <- "5000 individuals"


p1 <- res_bias10K[[1]]
p2 <- res_bias10K[[2]]
p3 <- res_bias10K[[3]]
p4 <- res_bias10K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df4 <- rbind(p1,p2,p3,p4)
df4$size <- "10000 individuals"

df_all <- rbind(df1,df2,df3,df4)


df_all <- df_all %>% 
  mutate(model = case_when(
    model == "flexsurv_EO" ~ "0",
     model == "flexsurv" ~ "a",
    model == "coxph" ~ "b",
    model == "msm"  ~ "c",
    model == "msm_age"  ~ "d",
    model == "nhm"  ~ "e",
    model == "imputation" ~ "f",
    TRUE ~ model  
  ))

latex_labels <- c(
    "1" = "Transition 1",
    "2" = "Transition 2",
    "3" = "Transition 3",
    "cov1_mean" = "hat(beta)[1]",
    "cov2_mean" = "hat(beta)[2]",
    "cov3_mean" = "hat(beta)[3]"
  )

df_all<- df_all %>%
   mutate(
    size = factor(size, levels = c("500 individuals", "2000 individuals", "5000 individuals","10000 individuals"))
    )

df_all <- df_all[df_all$size=="500 individuals",] #CHANGE HERE


df_all_long <- df_all %>%
  gather(key = "parameter", value = "bias_mean", cov1_mean, cov2_mean, cov3_mean) 

 plot <- ggplot(data = df_all_long, aes(x = model, y = bias_mean, color = scenario)) + 
  geom_point(size = 3, shape = 19) + 
  
  facet_grid(parameter ~ transition, scales = "free_y", 
             labeller = labeller(parameter = as_labeller(latex_labels, label_parsed), 
                                 transition = as_labeller(latex_labels))) + 
  
  labs(title = NULL, 
       x = "Model", 
       y = "Bias",
       color = "Observation Scheme") + 
  
  geom_line(aes(group = scenario), size = 1, linetype = "solid", alpha = 0.8) + 
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50", size = 1) + 
  #geom_errorbar(aes(ymin = bias_lower, ymax = bias_upper), width = 0.3, color = "black") + 
  
   
  theme_bw() + 
  theme(legend.position = "top", 
        axis.text.x = element_text(angle = 45, hjust = 1, size = 12), 
        plot.title = element_text(size = 14, hjust = 0.5),
        strip.text = element_text(size = 12),
        legend.title = element_text(size = 12, face = "bold"),
        legend.text = element_text(size = 10),
        panel.spacing = unit(1, "lines"),
        axis.text.y = element_text(size = 12),
        axis.title = element_text(size = 14),
        plot.caption = element_text(hjust = 0, size = 8)) + 
  
  scale_color_viridis_d(option = "B", begin = 0.2, end = 0.8)
 
  
plot
 ggsave("/Users/AlessandraPescina/OneDrive - Politecnico di Milano/ANNO 5/secondo semestre/TESI/Tesi/Tesi-KI/wrapper_MM/plots/bias_scheme.pdf", plot, width = 8, height = 6, units = "in", dpi = 300)
 
```

Absolute bias of covariates effect varying sample size for a chosen observational scheme
```{r}

p1 <- res_bias500[[1]]
p2 <- res_bias500[[2]]
p3 <- res_bias500[[3]]
p4 <- res_bias500[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df1 <- rbind(p1,p2,p3,p4)
df1$size <- "500 individuals"

p1 <- res_bias2K[[1]]
p2 <- res_bias2K[[2]]
p3 <- res_bias2K[[3]]
p4 <- res_bias2K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df2 <- rbind(p1,p2,p3,p4)
df2$size <- "2000 individuals"


p1 <- res_bias5K[[1]]
p2 <- res_bias5K[[2]]
p3 <- res_bias5K[[3]]
p4 <- res_bias5K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df3 <- rbind(p1,p2,p3,p4)
df3$size <- "5000 individuals"


p1 <- res_bias10K[[1]]
p2 <- res_bias10K[[2]]
p3 <- res_bias10K[[3]]
p4 <- res_bias10K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df4 <- rbind(p1,p2,p3,p4)
df4$size <- "10000 individuals"

df_all <- rbind(df1,df2,df3,df4)


df_all <- df_all %>% 
  mutate(model = case_when(
    model == "flexsurv_EO" ~ "0",
     model == "flexsurv" ~ "a",
    model == "coxph" ~ "b",
    model == "msm"  ~ "c",
    model == "msm_age"  ~ "d",
    model == "nhm"  ~ "e",
    model == "imputation" ~ "f",
    TRUE ~ model  # Keep other values unchanged
  ))

latex_labels <- c(
    "1" = "Transition 1",
    "2" = "Transition 2",
    "3" = "Transition 3",
    "cov1_mean" = "hat(beta)[1]",
    "cov2_mean" = "hat(beta)[2]",
    "cov3_mean" = "hat(beta)[3]"
  )

df_all<- df_all %>%
   mutate(
    size = factor(size, levels = c("500 individuals", "2000 individuals", "5000 individuals","10000 individuals"))
    )


df_all <- df_all[df_all$scenario=="1 year",]

df_all_long <- df_all %>%
  gather(key = "parameter", value = "bias_mean", cov1_mean, cov2_mean, cov3_mean) 

 plot <- ggplot(data = df_all_long, aes(x = model, y = bias_mean, color = size)) + 
  geom_point(size = 3, shape = 19) + 
  
  facet_grid(parameter ~ transition, scales = "free_y", 
             labeller = labeller(parameter = as_labeller(latex_labels, label_parsed), 
                                 transition = as_labeller(latex_labels))) + 
  
  labs(title = NULL, 
       x = "Model", 
       y = "Bias",
       color = "Sample size") + 
  
  geom_line(aes(group = size), size = 1, linetype = "solid", alpha = 0.8) + 
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50", size = 1) + 
  #geom_errorbar(aes(ymin = bias_lower, ymax = bias_upper), width = 0.3, color = "black") + 
  
   
  theme_bw() + 
  theme(legend.position = "top", 
        axis.text.x = element_text(angle = 45, hjust = 1, size = 12), 
        plot.title = element_text(size = 14, hjust = 0.5),
        strip.text = element_text(size = 12),
        legend.title = element_text(size = 12, face = "bold"),
        legend.text = element_text(size = 10),
        panel.spacing = unit(1, "lines"),
        axis.text.y = element_text(size = 12),
        axis.title = element_text(size = 14),
        plot.caption = element_text(hjust = 0, size = 8)) + 
  
  
  scale_color_viridis_d(option = "D", begin = 0.2, end = 0.8)
  
plot
 ggsave("/Users/AlessandraPescina/OneDrive - Politecnico di Milano/ANNO 5/secondo semestre/TESI/Tesi/Tesi-KI/wrapper_MM/plots/bias_size.pdf", plot, width = 8, height = 6, units = "in", dpi = 300)
 
```


### 95% Coverage of covariates effect

95% Coverage of covariates effect varying observational scheme for a chosen sample size
```{r}
p1 <- res_cov_ic500[[1]]
p2 <- res_cov_ic500[[2]]
p3 <- res_cov_ic500[[3]]
p4 <- res_cov_ic500[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df1 <- rbind(p1,p2,p3,p4)
df1$size <- "500 individuals"

p1 <- res_cov_ic2K[[1]]
p2 <- res_cov_ic2K[[2]]
p3 <- res_cov_ic2K[[3]]
p4 <- res_cov_ic2K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df2 <- rbind(p1,p2,p3,p4)
df2$size <- "2000 individuals"


p1 <- res_cov_ic5K[[1]]
p2 <- res_cov_ic5K[[2]]
p3 <- res_cov_ic5K[[3]]
p4 <- res_cov_ic5K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df3 <- rbind(p1,p2,p3,p4)
df3$size <- "5000 individuals"


p1 <- res_cov_ic10K[[1]]
p2 <- res_cov_ic10K[[2]]
p3 <- res_cov_ic10K[[3]]
p4 <- res_cov_ic10K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df4 <- rbind(p1,p2,p3,p4)
df4$size <- "10000 individuals"

df_all <- rbind(df1,df2,df3,df4)

df_all <- df_all %>% 
  mutate(model = case_when(
    model == "flexsurv_EO" ~ "0",
     model == "flexsurv" ~ "a",
    model == "coxph" ~ "b",
    model == "msm"  ~ "c",
    model == "msm_age"  ~ "d",
    model == "nhm"  ~ "e",
    model == "imputation" ~ "f",
    TRUE ~ model  # Keep other values unchanged
  ))

latex_labels <- c(
    "1" = "Transition 1",
    "2" = "Transition 2",
    "3" = "Transition 3",
    "cov1_mean" = "hat(beta)[1]",
    "cov2_mean" = "hat(beta)[2]",
    "cov3_mean" = "hat(beta)[3]"
  )

df_all<- df_all %>%
   mutate(
    size = factor(size, levels = c("500 individuals", "2000 individuals", "5000 individuals","10000 individuals"))
    )


df_all <- df_all[df_all$size=="500 individuals",]


df_all_long <- df_all %>%
  gather(key = "parameter", value = "coverage", cov1_mean, cov2_mean, cov3_mean) %>%
  select(model, transition, parameter, coverage, scenario, size)
df_all_long$coverage <- df_all_long$coverage*100

plot <- ggplot(data = df_all_long, aes(x = model, y = coverage, color = scenario)) +
  geom_point(size = 3, shape = 19) +
  geom_line(aes(group = scenario), size = 1, linetype = "dashed", alpha = 0.8) +
  geom_hline(yintercept = 95, linetype = "dashed", color = "grey50", size = 1) +
  
  facet_grid(parameter ~ transition, scales = "free_y",
             labeller = labeller(parameter = as_labeller(latex_labels, label_parsed),
                                 transition = as_labeller(latex_labels))) +
  
  labs(x = "Model", y = "Coverage (%)", color = "Sample Size") +
  
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
        plot.title = element_text(size = 14, hjust = 0.5),
        strip.text = element_text(size = 12),
        legend.title = element_text(size = 12, face = "bold"),
        legend.text = element_text(size = 10),
        panel.spacing = unit(1, "lines"),
        axis.text.y = element_text(size = 12),
        axis.title = element_text(size = 14),
        plot.caption = element_text(hjust = 0, size = 8)) +
  
  scale_color_viridis_d(option = "B", begin = 0.2, end = 0.8)

plot
 ggsave("/Users/AlessandraPescina/OneDrive - Politecnico di Milano/ANNO 5/secondo semestre/TESI/Tesi/Tesi-KI/wrapper_MM/plots/coverage_scheme.pdf", 
plot, width = 8, height = 6, units = "in", dpi = 300)

```
95% Coverage of covariates effect varying sample size for a chosen observational scheme

```{r}
p1 <- res_cov_ic500[[1]]
p2 <- res_cov_ic500[[2]]
p3 <- res_cov_ic500[[3]]
p4 <- res_cov_ic500[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df1 <- rbind(p1,p2,p3,p4)
df1$size <- "500 individuals"

p1 <- res_cov_ic2K[[1]]
p2 <- res_cov_ic2K[[2]]
p3 <- res_cov_ic2K[[3]]
p4 <- res_cov_ic2K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df2 <- rbind(p1,p2,p3,p4)
df2$size <- "2000 individuals"


p1 <- res_cov_ic5K[[1]]
p2 <- res_cov_ic5K[[2]]
p3 <- res_cov_ic5K[[3]]
p4 <- res_cov_ic5K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df3 <- rbind(p1,p2,p3,p4)
df3$size <- "5000 individuals"


p1 <- res_cov_ic10K[[1]]
p2 <- res_cov_ic10K[[2]]
p3 <- res_cov_ic10K[[3]]
p4 <- res_cov_ic10K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df4 <- rbind(p1,p2,p3,p4)
df4$size <- "10000 individuals"

df_all <- rbind(df1,df2,df3,df4)

df_all <- df_all %>% 
  mutate(model = case_when(
    model == "flexsurv_EO" ~ "0",
     model == "flexsurv" ~ "a",
    model == "coxph" ~ "b",
    model == "msm"  ~ "c",
    model == "msm_age"  ~ "d",
    model == "nhm"  ~ "e",
    model == "imputation" ~ "f",
    TRUE ~ model  # Keep other values unchanged
  ))

latex_labels <- c(
    "1" = "Transition 1",
    "2" = "Transition 2",
    "3" = "Transition 3",
    "cov1_mean" = "hat(beta)[1]",
    "cov2_mean" = "hat(beta)[2]",
    "cov3_mean" = "hat(beta)[3]"
  )

df_all<- df_all %>%
   mutate(
    size = factor(size, levels = c("500 individuals", "2000 individuals", "5000 individuals","10000 individuals"))
    )

df_all <- df_all[df_all$scenario=="1 year",]

df_all_long <- df_all %>%
  gather(key = "parameter", value = "coverage", cov1_mean, cov2_mean, cov3_mean) %>%
  select(model, transition, parameter, coverage, scenario, size)
df_all_long$coverage <- df_all_long$coverage*100

plot <- ggplot(data = df_all_long, aes(x = model, y = coverage, color = size)) +
  geom_point(size = 3, shape = 19) +
  geom_line(aes(group = size), size = 1, linetype = "dashed", alpha = 0.8) +
  geom_hline(yintercept = 95, linetype = "dashed", color = "grey50", size = 1) +
  
  facet_grid(parameter ~ transition, scales = "free_y",
             labeller = labeller(parameter = as_labeller(latex_labels, label_parsed),
                                 transition = as_labeller(latex_labels))) +
  
  labs(x = "Model", y = "Coverage (%)", color = "Observation Scheme") +
  
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
        plot.title = element_text(size = 14, hjust = 0.5),
        strip.text = element_text(size = 12),
        legend.title = element_text(size = 12, face = "bold"),
        legend.text = element_text(size = 10),
        panel.spacing = unit(1, "lines"),
        axis.text.y = element_text(size = 12),
        axis.title = element_text(size = 14),
        plot.caption = element_text(hjust = 0, size = 8)) +
  
  scale_color_viridis_d(option = "D", begin = 0.2, end = 0.8)

plot
 ggsave("/Users/AlessandraPescina/OneDrive - Politecnico di Milano/ANNO 5/secondo semestre/TESI/Tesi/Tesi-KI/wrapper_MM/plots/coverage_size.pdf", 
plot, width = 8, height = 6, units = "in", dpi = 300)

```


### Type I Error in different models 

Type I error for transition to Dementia and for transition from Dementia to Death 

```{r}
p1 <- plots_errorI500[[1]]
p2 <- plots_errorI500[[2]]
p3 <- plots_errorI500[[3]]
p4 <- plots_errorI500[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df1 <- rbind(p1,p2,p3,p4)
df1$size <- "500 individuals"

p1 <- plots_errorI2K[[1]]
p2 <- plots_errorI2K[[2]]
p3 <- plots_errorI2K[[3]]
p4 <- plots_errorI2K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df2 <- rbind(p1,p2,p3,p4)
df2$size <- "2000 individuals"

p1 <- plots_errorI5K[[1]]
p2 <- plots_errorI5K[[2]]
p3 <- plots_errorI5K[[3]]
p4 <- plots_errorI5K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df3 <- rbind(p1,p2,p3,p4)
df3$size <- "5000 individuals"

p1 <- plots_errorI10K[[1]]
p2 <- plots_errorI10K[[2]]
p3 <- plots_errorI10K[[3]]
p4 <- plots_errorI10K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df4 <- rbind(p1,p2,p3,p4)
df4$size <- "10000 individuals"


df_all <- rbind(df1,df2,df3,df4)

df_all <- df_all %>% 
  mutate(model = case_when(
    model == "flexsurv_EO" ~ "0",
     model == "flexsurv" ~ "a",
    model == "coxph" ~ "b",
    model == "msm"  ~ "c",
    model == "msm_age"  ~ "d",
    model == "nhm"  ~ "e",
    model == "imputation" ~ "f",
    TRUE ~ model  # Keep other values unchanged
  ))

latex_labels <- c(
    "1" = "Transition 1",
    "2" = "Transition 2",
    "3" = "Transition 3",
    "cov1" = "hat(beta)[1]",
    "cov2" = "hat(beta)[2]",
    "cov3" = "hat(beta)[3]"
  )

df_all<- df_all %>%
  mutate(
    power_category = factor(power_category, levels = c("Low (<5%)", "Moderate (5%-10%)", "High (>10%)"))
  )
df_all<- df_all %>%
  mutate(
    size = factor(size, levels = c("500 individuals", "2000 individuals", "5000 individuals","10000 individuals"))
  )

df_trans1 <- df_all[df_all$transition==1,]
df_trans3 <- df_all[df_all$transition==3,]

plot1 <- ggplot(df_trans1, aes(x = model, y = scenario, fill = power_category)) + 
  geom_tile(color = "white", width = 0.95, height = 0.95) +
  scale_fill_viridis_d(option = "D", begin = 0.85, end = 0.2)+
  
  facet_wrap(~ size, nrow = 2, ncol = 2, strip.position = "top") + 
  labs(
    title = NULL,  # from Dementia-free to Dementia
    x = "Model",
    y = "Observation scheme",
    fill = "Type I Error"
  ) + 
  theme_minimal() + 
  theme(
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1, color = "black"),
    axis.text.y = element_text(size = 12, color = "black"),  
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    strip.text = element_text(size = 12,  color = "black"), 
    legend.position = "top",
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    legend.key.size = unit(1, "lines"),  
    plot.margin = margin(20, 10, 20, 10),  
    panel.grid = element_blank(),  
    panel.background = element_blank()  
  )

plot1

plot2 <- ggplot(df_trans3, aes(x = model, y = scenario, fill = power_category)) + 
  geom_tile(color = "white", width = 0.95, height = 0.95) +
  scale_fill_viridis_d(option = "D", begin = 0.85, end = 0.2)+
  
  facet_wrap(~ size, nrow = 2, ncol = 2, strip.position = "top") + 
  labs(
    title = NULL,  # from Dementia-free to Dementia
    x = "Model",
    y = "Observation scheme",
    fill = "Type I Error"
  ) + 
  theme_minimal() + 
  theme(
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1, color = "black"),
    axis.text.y = element_text(size = 12, color = "black"),  
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    strip.text = element_text(size = 12,  color = "black"),  
    legend.position = "top",
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    legend.key.size = unit(1, "lines"),  
    plot.margin = margin(20, 10, 20, 10),  
    panel.grid = element_blank(),  
    panel.background = element_blank()  
  )

plot2

ggsave("/Users/AlessandraPescina/OneDrive - Politecnico di Milano/ANNO 5/secondo semestre/TESI/Tesi/Tesi-KI/wrapper_MM/plots/errortypeI_Beta1.pdf",  plot1,  width = 8, height = 6, units = "in", dpi = 300)
ggsave("/Users/AlessandraPescina/OneDrive - Politecnico di Milano/ANNO 5/secondo semestre/TESI/Tesi/Tesi-KI/wrapper_MM/plots/errortypeI_Beta2.pdf",  plot2,  width = 8, height = 6, units = "in", dpi = 300)

```


### Power of different models

Statistical Power for each transition

```{r}
p1 <- plots_power500[[1]]
p2 <- plots_power500[[2]]
p3 <- plots_power500[[3]]
p4 <- plots_power500[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df1 <- rbind(p1,p2,p3,p4)
df1$size <- "500 individuals"

p1 <- plots_power2K[[1]]
p2 <- plots_power2K[[2]]
p3 <- plots_power2K[[3]]
p4 <- plots_power2K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df2 <- rbind(p1,p2,p3,p4)
df2$size <- "2000 individuals"

p1 <- plots_power5K[[1]]
p2 <- plots_power5K[[2]]
p3 <- plots_power5K[[3]]
p4 <- plots_power5K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df3 <- rbind(p1,p2,p3,p4)
df3$size <- "5000 individuals"

p1 <- plots_power10K[[1]]
p2 <- plots_power10K[[2]]
p3 <- plots_power10K[[3]]
p4 <- plots_power10K[[4]]

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df4 <- rbind(p1,p2,p3,p4)
df4$size <- "10000 individuals"

df_all <- rbind(df1,df2,df3,df4)

df_all <- df_all %>% 
  mutate(model = case_when(
    model == "flexsurv_EO" ~ "0",
     model == "flexsurv" ~ "a",
    model == "coxph" ~ "b",
    model == "msm"  ~ "c",
    model == "msm_age"  ~ "d",
    model == "nhm"  ~ "e",
    model == "imputation" ~ "f",
    TRUE ~ model  
  ))


latex_labels <- c(
    "1" = "Transition 1",
    "2" = "Transition 2",
    "3" = "Transition 3",
    "cov1" = "hat(beta)[1]",
    "cov2" = "hat(beta)[2]",
    "cov3" = "hat(beta)[3]"
  )

df_all<- df_all %>%
  mutate(
    power_category = factor(power_category, levels = c("Low (<50%)", "Moderate (50%-80%)", "High (>80%)"))
  )
df_all<- df_all %>%
  mutate(
    size = factor(size, levels = c("500 individuals", "2000 individuals", "5000 individuals","10000 individuals"))
  )

df_trans1 <- df_all[df_all$transition==1,]
df_trans2 <- df_all[df_all$transition==2,]
df_trans3 <- df_all[df_all$transition==3,]

plot1 <- ggplot(df_trans1, aes(x = model, y = scenario, fill = power_category)) + 
  geom_tile(color = "white", width = 0.95, height = 0.95) +
  scale_fill_viridis_d(option = "D", begin = 0.2, end = 0.85)+
  facet_grid(rows = vars(covariate), cols = vars(size), 
             labeller = labeller(covariate = as_labeller(latex_labels, label_parsed))) +
  labs(
    title = NULL,  
    x = "Model",
    y = "Observation scheme",
    fill = "Power"
  ) + 
  theme_minimal() + 
  theme(
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1, color = "black"),
    axis.text.y = element_text(size = 12, color = "black"), 
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    strip.text = element_text(size = 12,  color = "black"),  
    legend.position = "top",
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    legend.key.size = unit(1, "lines"),  
    plot.margin = margin(20, 10, 20, 10),  
    panel.grid = element_blank(),  
    panel.background = element_blank()  
  )

plot1

ggsave("/Users/AlessandraPescina/OneDrive - Politecnico di Milano/ANNO 5/secondo semestre/TESI/Tesi/Tesi-KI/wrapper_MM/plots/powertrans1.pdf",plot1, width = 8, height = 6, units = "in", dpi = 300)

plot2 <- ggplot(df_trans2, aes(x = model, y = scenario, fill = power_category)) + 
  geom_tile(color = "white", width = 0.95, height = 0.95) +
  scale_fill_viridis_d(option = "D", begin = 0.2, end = 0.85)+
  facet_grid(rows = vars(covariate), cols = vars(size), 
             labeller = labeller(covariate = as_labeller(latex_labels, label_parsed))) +
  labs(
    title = NULL,  
    x = "Model",
    y = "Observation scheme",
    fill = "Power"
  ) + 
  theme_minimal() + 
  theme(
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1, color = "black"),
    axis.text.y = element_text(size = 12, color = "black"),  
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    strip.text = element_text(size = 12,  color = "black"),  
    legend.position = "top",
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    legend.key.size = unit(1, "lines"),  
    plot.margin = margin(20, 10, 20, 10),  
    panel.grid = element_blank(),  
    panel.background = element_blank()  
  )

plot2

ggsave("/Users/AlessandraPescina/OneDrive - Politecnico di Milano/ANNO 5/secondo semestre/TESI/Tesi/Tesi-KI/wrapper_MM/plots/powertrans2.pdf",plot2, width = 8, height = 6, units = "in", dpi = 300)

plot3 <- ggplot(df_trans3, aes(x = model, y = scenario, fill = power_category)) + 
  geom_tile(color = "white", width = 0.95, height = 0.95) +
  scale_fill_viridis_d(option = "D", begin = 0.2, end = 0.85)+
  facet_grid(rows = vars(covariate), cols = vars(size), 
             labeller = labeller(covariate = as_labeller(latex_labels, label_parsed))) +
  labs(
    title = NULL,  
    x = "Model",
    y = "Observation scheme",
    fill = "Power"
  ) + 
  theme_minimal() + 
  theme(
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1, color = "black"),
    axis.text.y = element_text(size = 12, color = "black"),  
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    strip.text = element_text(size = 12,  color = "black"),  
    legend.position = "top",
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 12),
    legend.key.size = unit(1, "lines"),  
    plot.margin = margin(20, 10, 20, 10),  
    panel.grid = element_blank(),  
    panel.background = element_blank()  
  )

plot3

ggsave("/Users/AlessandraPescina/OneDrive - Politecnico di Milano/ANNO 5/secondo semestre/TESI/Tesi/Tesi-KI/wrapper_MM/plots/powertrans3.pdf",plot3, width = 8, height = 6, units = "in", dpi = 300)

```


### Relative Bias of time spent in each state

```{r}
p1 <-  res_bias_lfe500[[1]][[1]]
p2 <-  res_bias_lfe500[[2]][[1]]
p3 <-  res_bias_lfe500[[3]][[1]]
p4 <-  res_bias_lfe500[[4]][[1]]

p1$dem <- 0
p2$dem <- 0
p3$dem <- 0
p4$dem <- 0

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df1_nodem <- rbind(p1,p2,p3,p4)

p1 <-  res_bias_lfe500[[1]][[2]]
p2 <-  res_bias_lfe500[[2]][[2]]
p3 <-  res_bias_lfe500[[3]][[2]]
p4 <-  res_bias_lfe500[[4]][[2]]

p1$dem <- 1
p2$dem <- 1
p3$dem <- 1
p4$dem <- 1

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df1_dem <- rbind(p1,p2,p3,p4)

df1 <- rbind(df1_nodem,df1_dem)
df1$size <- "500 individuals"

p1 <-  res_bias_lfe2K[[1]][[1]]
p2 <-  res_bias_lfe2K[[2]][[1]]
p3 <-  res_bias_lfe2K[[3]][[1]]
p4 <-  res_bias_lfe2K[[4]][[1]]

p1$dem <- 0
p2$dem <- 0
p3$dem <- 0
p4$dem <- 0

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df2_nodem <- rbind(p1,p2,p3,p4)

p1 <-  res_bias_lfe2K[[1]][[2]]
p2 <-  res_bias_lfe2K[[2]][[2]]
p3 <-  res_bias_lfe2K[[3]][[2]]
p4 <-  res_bias_lfe2K[[4]][[2]]

p1$dem <- 1
p2$dem <- 1
p3$dem <- 1
p4$dem <- 1

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df2_dem <- rbind(p1,p2,p3,p4)

df2 <- rbind(df2_nodem,df2_dem)
df2$size <- "2000 individuals"

p1 <-  res_bias_lfe5K[[1]][[1]]
p2 <- res_bias_lfe5K[[2]][[1]]
p3 <- res_bias_lfe5K[[3]][[1]]
p4 <- res_bias_lfe5K[[4]][[1]]

p1$dem <- 0
p2$dem <- 0
p3$dem <- 0
p4$dem <- 0

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df3_nodem <- rbind(p1,p2,p3,p4)

p1 <- res_bias_lfe5K[[1]][[2]]
p2 <- res_bias_lfe5K[[2]][[2]]
p3 <- res_bias_lfe5K[[3]][[2]]
p4 <- res_bias_lfe5K[[4]][[2]]

p1$dem <- 1
p2$dem <- 1
p3$dem <- 1
p4$dem <- 1

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df3_dem <- rbind(p1,p2,p3,p4)

df3 <- rbind(df3_nodem,df3_dem)
df3$size <- "5000 individuals"

p1 <-  res_bias_lfe10K[[1]][[1]]
p2 <- res_bias_lfe10K[[2]][[1]]
p3 <- res_bias_lfe10K[[3]][[1]]
p4 <- res_bias_lfe10K[[4]][[1]]

p1$dem <- 0
p2$dem <- 0
p3$dem <- 0
p4$dem <- 0

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df4_nodem <- rbind(p1,p2,p3,p4)

p1 <- res_bias_lfe10K[[1]][[2]]
p2 <- res_bias_lfe10K[[2]][[2]]
p3 <- res_bias_lfe10K[[3]][[2]]
p4 <- res_bias_lfe10K[[4]][[2]]

p1$dem <- 1
p2$dem <- 1
p3$dem <- 1
p4$dem <- 1

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df4_dem <- rbind(p1,p2,p3,p4)

df4 <- rbind(df4_nodem,df4_dem)
df4$size <- "10000 individuals"

df_all <- rbind(df1,df2,df3,df4)
df_all$dem <- as.factor(df_all$dem)

df_all<- df_all %>%
  mutate(
    size = factor(size, levels = c("500 individuals", "2000 individuals", "5000 individuals","10000 individuals"))
  )

df_all <- df_all %>% 
  mutate(model = case_when(
    model == "flexsurv_EO" ~ "0",
     model == "flexsurv" ~ "a",
    model == "coxph" ~ "b",
    model == "msm"  ~ "c",
    model == "msm_age"  ~ "d",
    model == "nhm"  ~ "e",
    model == "imputation" ~ "f",
    TRUE ~ model  
  ))

df_nodem <- df_all[df_all$dem==0,]
df_dem <- df_all[df_all$dem==1,]

p0 <- ggplot(df_nodem, aes(x = model, y = lfe, color = size)) +
  scale_colour_viridis_d(begin = 0.2, end=0.8)+
  geom_point(size = 3) + 
  geom_line(aes(group = size), size = 1, linetype = "dashed", alpha = 0.8) + 
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey") +  
  facet_wrap(~ scenario, ncol = 2) +  
  theme_minimal() +  
  theme(
    strip.text = element_text( size = 12), 
    axis.text = element_text(size = 10),  
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 10),
    legend.position = "top"
  ) +
  labs(title = NULL, 
       x = "Model", 
       y = "Relative Bias(%)", 
       color = "Sample Size")

p0
 ggsave("/Users/AlessandraPescina/OneDrive - Politecnico di Milano/ANNO 5/secondo semestre/TESI/Tesi/Tesi-KI/wrapper_MM/plots/T0.pdf", p0, 
       width = 8, height = 6, units = "in", dpi = 300)
 
p1 <- ggplot(df_dem, aes(x = model, y = lfe, color = size)) +
  scale_colour_viridis_d(begin = 0.2, end=0.8)+
  geom_point(size = 3) + 
  geom_line(aes(group = size), size = 1, linetype = "dashed", alpha = 0.8) + 
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey") +  
  facet_wrap(~ scenario, ncol = 2) +  
  theme_minimal() +  
  theme(
    strip.text = element_text( size = 12), 
    axis.text = element_text(size = 10),  
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 10),
    legend.position = "top"
  ) +
  labs(title = NULL, 
       x = "Model", 
       y = "Relative Bias(%)", 
       color = "Sample Size")

p1
 ggsave("/Users/AlessandraPescina/OneDrive - Politecnico di Milano/ANNO 5/secondo semestre/TESI/Tesi/Tesi-KI/wrapper_MM/plots/T1.pdf", p1, 
       width = 8, height = 6, units = "in", dpi = 300)

```


### Convergence of different models

```{r}
convergence500 <- rbind(combined_cov500[[1]],combined_cov500[[2]],combined_cov500[[3]],combined_cov500[[4]])
convergence500$size <- "500 individuals"
convergence500$scenario <- rep(2:5,each=100)

convergence2K <- rbind(combined_cov2K[[1]],combined_cov2K[[2]],combined_cov2K[[3]],combined_cov2K[[4]])
convergence2K$size <- "2000 individuals"
convergence2K$scenario <- rep(2:5,each=100)

convergence5K <- rbind(combined_cov5K[[1]],combined_cov5K[[2]],combined_cov5K[[3]],combined_cov5K[[4]])
convergence5K$size <- "5000 individuals"
convergence5K$scenario <- rep(2:5,each=100)

convergence10K <- rbind(combined_cov10K[[1]],combined_cov10K[[2]],combined_cov10K[[3]],combined_cov10K[[4]])
convergence10K$size <- "10000 individuals"
convergence10K$scenario <- rep(2:5,each=100)

tot_convergence <- rbind(convergence500,convergence2K,convergence5K,convergence10K)

tot_convergence<- tot_convergence %>%
  mutate(
    size = factor(size, levels = c("500 individuals", "2000 individuals", "5000 individuals","10000 individuals"))
  )

tot_convergence <- tot_convergence %>%
  mutate(a=coxph, b=flexsurv, c=msm, d=msm_age, e=nhm, f=imputation, coxph=NULL, flexsurv=NULL, msm=NULL, msm_age=NULL, nhm=NULL, imputation=NULL)

conv_long <- tot_convergence %>%
  pivot_longer(cols = c("a","b","c","d","e","f"),
               names_to = "model",
               values_to = "convergence")

conv_summary <- conv_long %>%
  group_by(size, model, convergence, scenario) %>%
  summarise(count = n(), .groups = "drop")%>%
  group_by(size, model, scenario) %>%
  mutate(percentage = count / sum(count) * 100)

conv_table <- conv_summary %>%
  select(scenario, size, model, convergence, percentage) %>%
  pivot_wider(names_from = convergence, values_from = percentage, values_fill = 0) %>%
  rename( "suboptimal" = "1", "Convergence" = "2")

conv_table <- conv_table %>%
  mutate(
     scenario = case_when(
        scenario == "2" ~ "1 year",
        scenario == "3" ~ "3 years",
        scenario == "4" ~ "3-6 years",
        scenario == "5" ~ "irregular",
        )) 
 

plot <- ggplot(conv_table, aes(x = model, y = scenario, fill = Convergence)) +
  geom_tile(color = "white") +
  facet_wrap(~size) +
  scale_fill_viridis_c(option = "D", begin = 0.1, end = 0.9, name = "Percentage (%)")+
  labs(
    title = NULL,
    x = "Model",
    y = "Observation Scheme"
  ) +
  theme_minimal()+
   theme(
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5), 
    legend.position = "top")

ggsave("/Users/AlessandraPescina/OneDrive - Politecnico di Milano/ANNO 5/secondo semestre/TESI/Tesi/Tesi-KI/wrapper_MM/plots/convergence.pdf", plot,
       width = 8, height = 6, units = "in", dpi = 300)
```

### Averaged computational time for different models

```{r}

computational_time500 <- rbind(ct_all_schemes500[[1]], ct_all_schemes500[[2]], ct_all_schemes500[[3]], ct_all_schemes500[[4]])
computational_time500 <- as.data.frame(computational_time500)
computational_time500$scheme <- rep(2:5, each=100)
mean_ct500 <- computational_time500 %>%
  group_by(scheme)%>%
  summarise(across(everything(), mean, na.rm = TRUE))

computational_time2K <- rbind(ct_all_schemes2K[[1]], ct_all_schemes2K[[2]], ct_all_schemes2K[[3]], ct_all_schemes2K[[4]])
computational_time2K <- as.data.frame(computational_time2K)
computational_time2K$scheme <- rep(2:5, each=100)
mean_ct2K <- computational_time2K %>%
  group_by(scheme)%>%
  summarise(across(everything(), mean, na.rm = TRUE))

computational_time5K <- rbind(ct_all_schemes5K[[1]], ct_all_schemes5K[[2]], ct_all_schemes5K[[3]], ct_all_schemes5K[[4]])
computational_time5K <- as.data.frame(computational_time5K)
computational_time5K$scheme <- rep(2:5, each=100)
mean_ct5K <- computational_time5K %>%
  group_by(scheme)%>%
  summarise(across(everything(), mean, na.rm = TRUE))

computational_time10K <- rbind(ct_all_schemes10K[[1]], ct_all_schemes10K[[2]], ct_all_schemes10K[[3]], ct_all_schemes10K[[4]])
computational_time10K <- as.data.frame(computational_time10K)
computational_time10K$scheme <- rep(2:5, each=100)
mean_ct10K <- computational_time10K %>%
  group_by(scheme)%>%
  summarise(across(everything(), mean, na.rm = TRUE))



t1 <- mean_ct500
t2 <- mean_ct2K
t3 <- mean_ct5K
t4 <- mean_ct10K

mean_ct_all <- rbind(t1,t2,t3,t4)
mean_ct_all$size <- rep(1:4, each=4)

colnames(mean_ct_all) <- c("scheme","a","b","c","d","e","f", "size")
mean_ct_all <- mean_ct_all%>%
  mutate(
    scheme = case_when(
      scheme == "2" ~ "1 year",
      scheme == "3" ~ "3 years",
      scheme == "4" ~ "3-6 years",
      scheme == "5" ~ "irregular",
      ))

mean_ct_all <- mean_ct_all%>%
  pivot_longer(cols=c("a","b","c","d","e","f"),
               names_to = "model",
               values_to = "time")

plot <- ggplot(mean_ct_all, aes(x = factor(size, labels = c("500", "2000", "5000", "10000")), 
                        y = time, color = model, group = model)) +
  geom_line(size = 1.2, alpha = 0.7) +
  geom_point(size = 3, alpha = 0.7)+

  facet_wrap(~ scheme, ncol = 2, scales = "fixed") + 
  scale_color_viridis_d() +
  labs(
    title = NULL,
    x = "Sample Size",
    y = "Time (s)",
    color = "Model"
  ) +
  theme_minimal(base_size = 14) + 
  theme(
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),  
  
    axis.title = element_text(size = 14), 
    axis.text = element_text(size = 10),  
    axis.text.x = element_text(angle = 45, hjust = 1), 
    legend.position = "top", 
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 10),  
    panel.grid.major = element_line(color = "gray80", linewidth = 0.5),  
    panel.grid.minor = element_blank()  
  )

ggsave("/Users/AlessandraPescina/OneDrive - Politecnico di Milano/ANNO 5/secondo semestre/TESI/Tesi/Tesi-KI/wrapper_MM/plots/comp_time.pdf", plot,
       width = 8, height = 6, units = "in", dpi = 300)
```

