---
title: "Performance Comparison"
author: "Alessandra Pescina"
date: "2024-12-16"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(fs)
library(parallel)
library(ggplot2)
library(dplyr)
library(tidyr)
library(patchwork)
library(here)
library(kableExtra)
library(plotly)
```

```{r}
setwd(here())

path <- "./wrapper_MM/plots_500/"
files <- list.files(path, pattern = "\\.RData$", full.names = TRUE)
lapply(files, load, .GlobalEnv)

conv_table500 <- conv_table
remove(conv_table)

mean_ct500 <- mean_ct
remove(mean_ct)

plots_bias500 <- plots_bias
remove(plots_bias)

plots_cov500 <- plots_cov
remove(plots_cov)

plots_errorI500 <- plots_errorI
remove(plots_errorI)

plots_power500 <- plots_power
remove(plots_power)

plots_distr500 <- plots_distr
remove(plots_distr)

plfe500 <- plfe
remove(plfe)

```


```{r}
path <- "./wrapper_MM/plots_2K/"
files <- list.files(path, pattern = "\\.RData$", full.names = TRUE)
lapply(files, load, .GlobalEnv)

conv_table2K <- conv_table
remove(conv_table)

mean_ct2K <- mean_ct
remove(mean_ct)

plots_bias2K <- plots_bias
remove(plots_bias)

plots_cov2K <- plots_cov
remove(plots_cov)

plots_errorI2K <- plots_errorI
remove(plots_errorI)

plots_power2K <- plots_power
remove(plots_power)

plots_distr2K <- plots_distr
remove(plots_distr)

plfe2K <- plfe
remove(plfe)


```


```{r}
path <- "./wrapper_MM/plots_5K/"
files <- list.files(path, pattern = "\\.RData$", full.names = TRUE)
lapply(files, load, .GlobalEnv)

conv_table5K <- conv_table
remove(conv_table)

mean_ct5K <- mean_ct
remove(mean_ct)

plots_bias5K<- plots_bias
remove(plots_bias)

plots_cov5K <- plots_cov
remove(plots_cov)

plots_errorI5K <- plots_errorI
remove(plots_errorI)

plots_power5K <- plots_power
remove(plots_power)

plots_distr5K <- plots_distr
remove(plots_distr)

plfe5K <- plfe
remove(plfe)

```


```{r}
path <- "./wrapper_MM/plots_10K/"
files <- list.files(path, pattern = "\\.RData$", full.names = TRUE)
lapply(files, load, .GlobalEnv)

conv_table10K <- conv_table
remove(conv_table)

mean_ct10K <- mean_ct
remove(mean_ct)

plots_bias10K<- plots_bias
remove(plots_bias)

plots_cov10K <- plots_cov
remove(plots_cov)

plots_errorI10K <- plots_errorI
remove(plots_errorI)

plots_power10K <- plots_power
remove(plots_power)

plots_distr10K <- plots_distr
remove(plots_distr)

plfe10K <- plfe
remove(plfe)

```

### Plots 500 observations

BIAS 500
```{r}
p1 <- plots_bias500[[1]] + labs(title= "1 year observation scheme")
p2 <- plots_bias500[[3]] + labs(title= "3 years observation scheme")
p3 <- plots_bias500[[5]] + labs(title= "3-6 years observation scheme")
p4 <- plots_bias500[[7]] + labs(title= "irregular observation scheme")
bias_500 <- (p1+p2) / (p3+p4) + plot_layout(guides = "collect")
bias_500 &
  ylim(0, 4)


```

```{r}

p1 <- plots_bias500[[1]]$data
p2 <- plots_bias500[[3]]$data
p3 <- plots_bias500[[5]]$data
p4 <- plots_bias500[[7]]$data

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df_all <- rbind(p1,p2,p3,p4)
latex_labels <- c(
    "1" = "Transition 1",
    "2" = "Transition 2",
    "3" = "Transition 3",
    "cov1" = "beta[1]",
    "cov2" = "beta[2]",
    "cov3" = "beta[3]"
  )


 ggplot(data = df_all, aes(x = model, y = bias_mean, color = scenario)) + 
  geom_point(size = 3, shape = 19) + 
  
  facet_grid(parameter ~ transition, scales = "free", 
             labeller = labeller(parameter = as_labeller(latex_labels, label_parsed), 
                                 transition = as_labeller(latex_labels))) + 
  
  labs(title = "Bias of the estimates", 
       x = "Model", 
       y = "Bias",
       color = "Observation Scheme") + 
  
  geom_line(aes(group = scenario), size = 1, linetype = "solid", alpha = 0.8) + 
  
  #geom_errorbar(aes(ymin = bias_lower, ymax = bias_upper), width = 0.3, color = "black") + 

  theme_bw() + 
  theme(legend.position = "top", 
        axis.text.x = element_text(angle = 45, hjust = 1, size = 12), 
        plot.title = element_text(size = 14, hjust = 0.5),
        strip.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10),
        panel.spacing = unit(1, "lines"),
        axis.text.y = element_text(size = 12),
        axis.title = element_text(size = 14)) + 
  
  scale_color_viridis_d(option = "B", begin = 0.2, end = 0.8)

```



COVERAGE 500
```{r, warning=FALSE}
p1 <- plots_cov500[[1]] + labs(title= "1 year observation scheme")
p2 <- plots_cov500[[2]] + labs(title= "3 years observation scheme")
p3 <- plots_cov500[[3]] + labs(title= "3-6 years observation scheme")
p4 <- plots_cov500[[4]] + labs(title= "irregular observation scheme")


cov_500 <- (p1+p2) / (p3+p4) + plot_layout(guides = "collect") 
cov_500
```

ERROR TYPE I 500
```{r}
p1 <- plots_errorI500[[1]][[1]] + labs(title = NULL,  x = "1 year observation scheme")+ theme(legend.position = "none")
p2 <- plots_errorI500[[2]][[1]] + labs(title = NULL,  x = "3 years observation scheme") 
p3 <- plots_errorI500[[3]][[1]] + labs(title = NULL, x = "3-6 years observation scheme")
p4 <- plots_errorI500[[4]][[1]] + labs(title = NULL,  x = "irregular observation scheme") 

typeIerror_500_trans1 <- (p1 + p2) / (p3 + p4) +
                  plot_layout(guides = "collect", widths = unit(rep(1, 4), "null")) +
                  plot_annotation(
                    title ="Heatmap of Type I Error by Method and Covariate for transition Dementia-free -> Dementia", 
                    theme = theme(plot.title = element_text(size = 15, hjust = 0.5)),
                  ) 
p1 <- plots_errorI500[[1]][[2]] + labs(title = NULL,  x = "1 year observation scheme") + theme(legend.position = "none")
p2 <- plots_errorI500[[2]][[2]] + labs(title = NULL,  x = "3 years observation scheme") 
p3 <- plots_errorI500[[3]][[2]] + labs(title = NULL, x = "3-6 years observation scheme") 
p4 <- plots_errorI500[[4]][[2]] + labs(title = NULL,  x = "irregular observation scheme") 

typeIerror_500_trans3 <- (p1 + p2 )/ (p3 + p4) +
                  plot_layout(guides = "collect", widths = unit(rep(1, 4), "null")) +
                  plot_annotation(
                    title ="Heatmap of Type I Error by Method and Covariate for transition Dementia -> Death", 
                    theme = theme(plot.title = element_text(size = 15, hjust = 0.5)),
                  ) 


typeIerror_500_trans1
typeIerror_500_trans3

```
```{r}
p1 <- plots_errorI500[[1]][[1]]$data
p1$scenario <- "1 year"
p2 <- plots_errorI500[[2]][[1]]$data
p2$scenario <- "3 years"
p3 <- plots_errorI500[[3]][[1]]$data
p3$scenario <- "3-6 years"
p4 <- plots_errorI500[[4]][[1]]$data
p4$scenario <- "irregular"

df1 <- rbind(p1,p2,p3,p4)
df1 <- df1 %>%
  mutate(
    power_category = factor(power_category, levels = c("Low (<5%)", "Moderate (5%-10%)", "High (>10%)"))
  )

p1 <- plots_errorI500[[1]][[2]]$data
p1$scenario <- "1 year"
p2 <- plots_errorI500[[2]][[2]]$data
p2$scenario <- "3 years"
p3 <- plots_errorI500[[3]][[2]]$data
p3$scenario <- "3-6 years"
p4 <- plots_errorI500[[4]][[2]]$data
p4$scenario <- "irregular"

df2 <- rbind(p1,p2,p3,p4)
df2 <- df2 %>%
  mutate(
    power_category = factor(power_category, levels = c("Low (<5%)", "Moderate (5%-10%)", "High (>10%)"))
  )



ggplot(df1, aes(x = model, y = power_category, color = scenario)) +
  geom_point(size = 4, position = position_dodge(width = 0.7)) +
  scale_color_viridis_d(option = "B", begin = 0.2, end = 0.8)+
  labs(
    title = "Error type I by Observation scheme",
    x = "Model",
    y = NULL,
    color = "Observation scheme",
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    axis.text.x = element_text(size = 12, angle = 45, hjust = 1),
    axis.text.y = element_text(size = 12),
    legend.position = "top"
  )
```

```{r}
df1$scenario <- factor(df1$scenario, levels = c("irregular", "3-6 years", "3 years", "1 year"))
df2$scenario <- factor(df2$scenario, levels = c("irregular", "3-6 years", "3 years", "1 year"))


plot1 <- ggplot(df1, aes(x = model, y = power_category, fill = power_category,  group = interaction(model, covariate))) +
  geom_bar(stat = "identity", color = "black", position = position_dodge(), aes(y=1)) +  # Aggiungi il bordo nero per le barre
 scale_fill_manual(
    values = c(
      "Low (<5%)" = "#8BC34A",  # Muted olive green
      "Moderate (5%-10%)" = "#FFEB3B",  # Warm golden yellow
      "High (>10%)" = "#E57373"  # Soft coral red
    )
  ) +
  
facet_wrap(~ scenario, ncol = 1, strip.position = "left") + 
  labs(
    title = "Type I Error by Model and Observation Scheme",
    subtitle = "Transition from Dementia-free to Dementia",
    x = "Model",
    y = "Observation scheme",
    fill = "Category"
  ) +
  theme_minimal() +
 theme(
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5, margin = margin(b = 15)),
    plot.subtitle = element_text(size = 12, hjust = 0.5, margin = margin(b = 15)),
    axis.text.x = element_text(size = 10, angle = 0, hjust = 1, color = "black"),
    axis.text.y = element_blank(),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    strip.text.y = element_text(size = 12, angle = 0, face = "italic", hjust = 1, color = "black"),
    strip.text.x = element_text(size = 12, face = "italic", color = "black"),
    legend.position = element_blank(),
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 8),
    legend.key.size = unit(1, "lines"),  # Increase legend key size
    plot.margin = margin(20, 10, 20, 10)  # Add margin around the plot for spacing
  )


plot2 <- ggplot(df2, aes(x = model, y = power_category, fill = power_category,  group = interaction(model, covariate))) +
  geom_bar(stat = "identity", color = "black", position = position_dodge(), aes(y=1)) +  # Aggiungi il bordo nero per le barre
 scale_fill_manual(
    values = c(
      "Low (<5%)" = "#8BC34A",  # Muted olive green
      "Moderate (5%-10%)" = "#FFEB3B",  # Warm golden yellow
      "High (>10%)" = "#E57373"  # Soft coral red
    )
  ) +
  
facet_wrap(~ scenario, ncol = 1, strip.position = "left") + 
  labs(
    title = "Type I Error by Model and Observation Scheme",
    subtitle = "Transition from Dementia to Death",
    x = "Model",
    y = "Observation scheme",
    fill = "Category"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5, margin = margin(b = 15)),
    plot.subtitle = element_text(size = 12, hjust = 0.5, margin = margin(b = 15)),
    axis.text.x = element_text(size = 10, angle = 0, hjust = 1, color = "black"),
    axis.text.y = element_blank(),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    strip.text.y = element_text(size = 12, angle = 0, face = "italic", hjust = 1, color = "black"),
    strip.text.x = element_text(size = 12, face = "italic", color = "black"),
    legend.position = element_blank(),
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 8),
    legend.key.size = unit(1, "lines"),  # Increase legend key size
    plot.margin = margin(20, 10, 20, 10)  # Add margin around the plot for spacing
  )

plot1 <- plot1 + theme(legend.position = "none", plot.title = element_blank())  
plot2 <- plot2 + theme(legend.position = "right", plot.title = element_blank())  

combined_plot <- (plot1 | plot2) +plot_layout(guides = 'collect')

combined_plot & 
  plot_annotation( title = "Type I Error by Model and Observation Scheme",
                   theme = theme(plot.title = element_text(size = 18, face = "bold", hjust = 0.5)))

 
```


POWER 500

```{r}
p1 <- plots_power500[[1]] + labs(title =NULL, x = "1 year observation scheme")
p2 <- plots_power500[[4]] + labs(title =NULL, x = "3 years observation scheme")
p3 <- plots_power500[[7]] + labs(title =NULL, x = "3-6 years observation scheme")
p4 <- plots_power500[[10]] +labs(title =NULL, x = "irregular observation scheme")

power_500_trans1 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Heatmap of Power by Method and Covariate for transition Dementia-free -> Dementia",  
  theme = theme(plot.title = element_text(size = 15, hjust = 0.5)))+  
  plot_layout(guides = "collect")

p1 <- plots_power500[[2]] + labs(title =NULL, x = "1 year observation scheme")
p2 <- plots_power500[[5]] + labs(title =NULL, x = "3 years observation scheme")
p3 <- plots_power500[[8]] + labs(title =NULL, x = "3-6 years observation scheme")
p4 <- plots_power500[[11]] +labs(title =NULL, x = "irregular observation scheme")

power_500_trans2 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Heatmap of Power by Method and Covariate for transition Dementia-free -> Death",  
  theme = theme(plot.title = element_text(size = 15, hjust = 0.5)))+  
  plot_layout(guides = "collect")

p1 <- plots_power500[[3]] + labs(title =NULL, x = "1 year observation scheme")
p2 <- plots_power500[[6]] + labs(title =NULL, x = "3 years observation scheme")
p3 <- plots_power500[[9]] + labs(title =NULL, x = "3-6 years observation scheme")
p4 <- plots_power500[[12]] +labs(title =NULL, x = "irregular observation scheme")

power_500_trans3 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Heatmap of Power by Method and Covariate for transition Dementia -> Death",  
  theme = theme(plot.title = element_text(size = 15, hjust = 0.5)))+  
  plot_layout(guides = "collect")
  
power_500_trans1
power_500_trans2
power_500_trans3
```
```{r}
p1 <- plots_power500[[1]]$data
p2 <- plots_power500[[4]]$data
p3 <- plots_power500[[7]]$data
p4 <- plots_power500[[10]]$data

p1$scenario <- "1 year"
p2$scenario <- "3 years"
p3$scenario <- "3-6 years"
p4$scenario <- "irregular"

df1 <- rbind(p1,p2,p3,p4) #dementia-free to dem
df1 <- df1 %>%
  mutate(
    power_category = factor(power_category, levels = c("Low (<50%)", "Moderate (50%-80%)", "High (>80%)"))
  )

p1 <- plots_power500[[2]]$data
p2 <- plots_power500[[5]]$data
p3 <- plots_power500[[8]]$data
p4 <- plots_power500[[11]]$data

p1$scenario <- "1 year"
p2$scenario <- "3 years"
p3$scenario <- "3-6 years"
p4$scenario <- "irregular"

df2 <- rbind(p1,p2,p3,p4) #dementia-free to death
df2 <- df2 %>%
  mutate(
    power_category = factor(power_category, levels = c("Low (<50%)", "Moderate (50%-80%)", "High (>80%)"))
  )

p1 <- plots_power500[[3]]$data
p2 <- plots_power500[[6]]$data
p3 <- plots_power500[[9]]$data
p4 <- plots_power500[[12]]$data

p1$scenario <- "1 year"
p2$scenario <- "3 years"
p3$scenario <- "3-6 years"
p4$scenario <- "irregular"

df3 <- rbind(p1,p2,p3,p4) #dementia to death
df3 <- df3 %>%
  mutate(
    power_category = factor(power_category, levels = c("Low (<50%)", "Moderate (50%-80%)", "High (>80%)"))
  )

df1$scenario <- factor(df1$scenario, levels = c("irregular", "3-6 years", "3 years", "1 year"))
df2$scenario <- factor(df2$scenario, levels = c("irregular", "3-6 years", "3 years", "1 year"))
df3$scenario <- factor(df3$scenario, levels = c("irregular", "3-6 years", "3 years", "1 year"))

latex_labels <- c(
  "beta[1]" = "beta[1]",
  "beta[2]" = "beta[2]",
  "beta[3]" = "beta[3]"
)

create_power_plot <- function(data, subtitle){
  ggplot(data, aes(x = model, y = power_category, fill = power_category)) + 
  geom_bar(stat = "identity", color = "black", position = position_dodge(), aes(y = 1)) +  # Add bar borders
  scale_fill_manual(
    values = c(
      "Low (<50%)" = "#E57373",        
      "Moderate (50%-80%)" = "#FFEB3B",       
      "High (>80%)" =  "#8BC34A"      
    )
  ) + 
  facet_grid(
    scenario ~ covariate, 
    labeller = labeller(covariate = as_labeller(latex_labels, label_parsed)),
    switch ="y"
  ) + 
  labs(
    title = "Power by Model and Observation Scheme",
    subtitle = subtitle,
    x = "Model",
    y = "Observation scheme",
    fill = "Category"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5, margin = margin(b = 15)),
    plot.subtitle = element_text(size = 12, hjust = 0.5, margin = margin(b = 15)),
    axis.text.x = element_text(size = 10, angle = 0, hjust = 1, color = "black"),
    axis.text.y = element_blank(),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    strip.text.y = element_text(size = 12, angle = 0, face = "italic", hjust = 1, color = "black"),
    strip.text.x = element_text(size = 12, face = "italic", color = "black"),
    legend.position = element_blank(),
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 8),
    legend.key.size = unit(1, "lines"),  # Increase legend key size
    plot.margin = margin(20, 10, 20, 10)  # Add margin around the plot for spacing
  )
}

plot1 <- create_power_plot(df1, "Transition from Dementia-free status to Dementia") 
plot2 <- create_power_plot(df2, "Transition from Dementia-free status to Death")
plot3 <- create_power_plot(df3, "Transition from Dementia status to Death")

plot1 <- plot1 + theme(legend.position = "none", plot.title = element_blank())  
plot3 <- plot3 + theme(legend.position = "none", plot.title = element_blank())  
plot2 <- plot2 + theme(legend.position = "right", plot.title = element_blank())  


combined_plot <- (plot1 | plot2 | plot3) +plot_layout(guides = 'collect')

combined_plot & 
  plot_annotation( title = "Power by Model and Observation Scheme",
                   theme = theme(plot.title = element_text(size = 18, face = "bold", hjust = 0.5)))
```


COEFFICIENTS DISTRIBUTION 500
```{r, warning=FALSE, message=FALSE} 
p1 <- plots_distr500[[1]][[1]] + 
  labs(title = NULL, x = "1 year observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p2 <- plots_distr500[[2]][[1]] + 
  labs(title = NULL, x = "3 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p3 <- plots_distr500[[3]][[1]] + 
  labs(title = NULL, x = "3-6 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p4 <- plots_distr500[[4]][[1]] + 
  labs(title = NULL, x = "irregular observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

distr_500_trans1 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Coefficients density distribution for transition Dementia-free to Dementia",  
  theme = theme(plot.title = element_text(size = 14, face = "bold", hjust = 0.5)))+  
  plot_layout(guides = "collect")

p1 <- plots_distr500[[1]][[2]] + 
  labs(title = NULL, x = "1 year observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p2 <- plots_distr500[[2]][[2]] + 
  labs(title = NULL, x = "3 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p3 <- plots_distr500[[3]][[2]] + 
  labs(title = NULL, x = "3-6 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p4 <- plots_distr500[[4]][[2]] + 
  labs(title = NULL, x = "irregular observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

distr_500_trans2 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Coefficients density distribution for transition Dementia-free to Death",  
  theme = theme(plot.title = element_text(size = 14, face = "bold", hjust = 0.5)))+  
  plot_layout(guides = "collect")

p1 <- plots_distr500[[1]][[3]] + 
  labs(title = NULL, x = "1 year observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p2 <- plots_distr500[[2]][[3]] + 
  labs(title = NULL, x = "3 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p3 <- plots_distr500[[3]][[3]] + 
  labs(title = NULL, x = "3-6 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p4 <- plots_distr500[[4]][[3]] + 
  labs(title = NULL, x = "irregular observation scheme") + 
  theme(axis.title.x = element_text(size = 8))
distr_500_trans3 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Coefficients density distribution for transition Dementia to Death",  
  theme = theme(plot.title = element_text(size = 14, face = "bold", hjust = 0.5)))+ 
  plot_layout(guides = "collect")
  
distr_500_trans1
distr_500_trans2
distr_500_trans3
```


```{r,warning=FALSE, message=FALSE} 

create_distr_plot <- function(plot, caption_text) {
  plot + 
    labs(
      title = NULL, 
      caption = caption_text  
    ) + 
    theme(
      axis.title.x = element_text(size = 8, face = "bold"), 
      axis.text.x = element_text(size = 8), 
      axis.text.y = element_text(size = 7), 
      plot.caption = element_text(size = 9, hjust = 0.5, vjust = 0.5, face = "bold"),
      plot.margin = margin(10, 10, 10, 10)  
    )
}

p1 <- create_distr_plot(plots_distr500[[1]][[1]], "1 year observation scheme")
p2 <- create_distr_plot(plots_distr500[[2]][[1]], "3 years observation scheme")
p3 <- create_distr_plot(plots_distr500[[3]][[1]], "3-6 years observation scheme")
p4 <- create_distr_plot(plots_distr500[[4]][[1]], "irregular observation scheme")

distr_500_trans1 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + 
  plot_annotation(
    title = "Coefficients Density Distribution for Transition Dementia-free to Dementia",
    theme = theme(plot.title = element_text(size = 13, face = "bold", hjust = 0.5)) 
  )

#
p1 <- create_distr_plot(plots_distr500[[1]][[2]], "1 year observation scheme")
p2 <- create_distr_plot(plots_distr500[[2]][[2]], "3 years observation scheme")
p3 <- create_distr_plot(plots_distr500[[3]][[2]], "3-6 years observation scheme")
p4 <- create_distr_plot(plots_distr500[[4]][[2]], "irregular observation scheme")

# Combine the plots for transition Dementia-free -> Death
distr_500_trans2 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + 
  plot_annotation(
    title = "Coefficients Density Distribution for Transition Dementia-free to Death",
    theme = theme(plot.title = element_text(size = 13, face = "bold", hjust = 0.5))  
  )


p1 <- create_distr_plot(plots_distr500[[1]][[3]], "1 year observation scheme")
p2 <- create_distr_plot(plots_distr500[[2]][[3]], "3 years observation scheme")
p3 <- create_distr_plot(plots_distr500[[3]][[3]], "3-6 years observation scheme")
p4 <- create_distr_plot(plots_distr500[[4]][[3]], "irregular observation scheme")

# Combine the plots for transition Dementia to Death
distr_500_trans3 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + 
  plot_annotation(
    title = "Coefficients Density Distribution for Transition Dementia to Death",
    theme = theme(plot.title = element_text(size = 13, face = "bold", hjust = 0.5))  
  )


distr_500_trans1 
distr_500_trans2 
distr_500_trans3 
 


```



### Plots 2K observations

BIAS_2K
```{r}
p1 <- plots_bias2K[[1]] + labs(title= "1 year observation scheme")
p2 <- plots_bias2K[[3]] + labs(title= "3 years observation scheme")
p3 <- plots_bias2K[[5]] + labs(title= "3-6 years observation scheme")
p4 <- plots_bias2K[[7]] + labs(title= "irregular observation scheme")

plots_bias_2K <- (p1+p2) / 
                 (p3+p4) +
                 plot_layout(guides = "collect")
plots_bias_2K & 
  ylim(0, 2)
```

```{r}

p1 <- plots_bias2K[[1]]$data
p2 <- plots_bias2K[[3]]$data
p3 <- plots_bias2K[[5]]$data
p4 <- plots_bias2K[[7]]$data

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df_all <- rbind(p1,p2,p3,p4)
latex_labels <- c(
    "1" = "Transition 1",
    "2" = "Transition 2",
    "3" = "Transition 3",
    "cov1" = "beta[1]",
    "cov2" = "beta[2]",
    "cov3" = "beta[3]"
  )


 ggplot(data = df_all, aes(x = model, y = bias_mean, color = scenario)) + 
  geom_point(size = 3, shape = 19) + 
  
  facet_grid(parameter ~ transition, scales = "free", 
             labeller = labeller(parameter = as_labeller(latex_labels, label_parsed), 
                                 transition = as_labeller(latex_labels))) + 
  
  labs(title = "Bias of the estimates", 
       x = "Model", 
       y = "Bias",
       color = "Observation Scheme") + 
  
  geom_line(aes(group = scenario), size = 1, linetype = "solid", alpha = 0.8) + 
  
  #geom_errorbar(aes(ymin = bias_lower, ymax = bias_upper), width = 0.3, color = "black") + 

  theme_bw() + 
  theme(legend.position = "top", 
        axis.text.x = element_text(angle = 45, hjust = 1, size = 12), 
        plot.title = element_text(size = 14, hjust = 0.5),
        strip.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10),
        panel.spacing = unit(1, "lines"),
        axis.text.y = element_text(size = 12),
        axis.title = element_text(size = 14)) + 
  
  scale_color_viridis_d(option = "B", begin = 0.2, end = 0.8)

```

COVERAGE 2K
```{r, warning=FALSE}
p1 <- plots_cov2K[[1]] + labs(title= "1 year observation scheme")
p2 <- plots_cov2K[[2]] + labs(title= "3 years observation scheme")
p3 <- plots_cov2K[[3]] + labs(title= "3-6 years observation scheme")
p4 <- plots_cov2K[[4]] + labs(title= "irregular observation scheme")

cov_2K <- (p1+p2) / (p3+p4) + plot_layout(guides = "collect")
cov_2K
```

ERROR TYPE I 2K
```{r}
p1 <- plots_errorI2K[[1]][[1]] + labs(title = NULL,  x = "1 year observation scheme")+ theme(legend.position = "none")
p2 <- plots_errorI2K[[2]][[1]] + labs(title = NULL,  x = "3 years observation scheme") 
p3 <- plots_errorI2K[[3]][[1]] + labs(title = NULL, x = "3-6 years observation scheme")
p4 <- plots_errorI2K[[4]][[1]] + labs(title = NULL,  x = "irregular observation scheme") 

typeIerror_2K_trans1 <- (p1 + p2) / (p3 + p4) +
                  plot_layout(guides = "collect", widths = unit(rep(1, 4), "null")) +
                  plot_annotation(
                    title ="Heatmap of Type I Error by Method and Covariate for transition Dementia-free -> Dementia", 
                    theme = theme(plot.title = element_text(size = 15, hjust = 0.5)),
                  ) 
p1 <- plots_errorI2K[[1]][[2]] + labs(title = NULL,  x = "1 year observation scheme") 
p2 <- plots_errorI2K[[2]][[2]] + labs(title = NULL,  x = "3 years observation scheme") + theme(legend.position = "none")
p3 <- plots_errorI2K[[3]][[2]] + labs(title = NULL, x = "3-6 years observation scheme") + theme(legend.position = "none")
p4 <- plots_errorI2K[[4]][[2]] + labs(title = NULL,  x = "irregular observation scheme") + theme(legend.position = "none")

typeIerror_2K_trans3 <- (p1 + p2 )/ (p3 + p4) +
                  plot_layout(guides = "collect", widths = unit(rep(1, 4), "null")) +
                  plot_annotation(
                    title ="Heatmap of Type I Error by Method and Covariate for transition Dementia -> Death", 
                    theme = theme(plot.title = element_text(size = 15, hjust = 0.5)),
                  ) 


typeIerror_2K_trans1
typeIerror_2K_trans3

```

POWER 2K
```{r}
p1 <- plots_power2K[[1]] + labs(title =NULL, x = "1 year observation scheme")
p2 <- plots_power2K[[4]] + labs(title =NULL, x = "3 years observation scheme")
p3 <- plots_power2K[[7]] + labs(title =NULL, x = "3-6 years observation scheme")
p4 <- plots_power2K[[10]] +labs(title =NULL, x = "irregular observation scheme")

power_2K_trans1 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Heatmap of Power by Method and Covariate for transition Dementia-free -> Dementia",  
  theme = theme(plot.title = element_text(size = 15, hjust = 0.5)))+  
  plot_layout(guides = "collect")

p1 <- plots_power2K[[2]] + labs(title =NULL, x = "1 year observation scheme")
p2 <- plots_power2K[[5]] + labs(title =NULL, x = "3 years observation scheme")+ theme(legend.position = "none")
p3 <- plots_power2K[[8]] + labs(title =NULL, x = "3-6 years observation scheme")+ theme(legend.position = "none")
p4 <- plots_power2K[[11]] +labs(title =NULL, x = "irregular observation scheme")

power_2K_trans2 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Heatmap of Power by Method and Covariate for transition Dementia-free -> Death",  
  theme = theme(plot.title = element_text(size = 15, hjust = 0.5)))+  
  plot_layout(guides = "collect")

p1 <- plots_power2K[[3]] + labs(title =NULL, x = "1 year observation scheme")
p2 <- plots_power2K[[6]] + labs(title =NULL, x = "3 years observation scheme")
p3 <- plots_power2K[[9]] + labs(title =NULL, x = "3-6 years observation scheme")
p4 <- plots_power2K[[12]] +labs(title =NULL, x = "irregular observation scheme")

power_2K_trans3 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Heatmap of Power by Method and Covariate for transition Dementia -> Death",  
  theme = theme(plot.title = element_text(size = 15, hjust = 0.5)))+  
  plot_layout(guides = "collect")
  
power_2K_trans1
power_2K_trans2
power_2K_trans3
```

COEFFICIENTS DISTRIBUTION 2K
```{r, warning=FALSE, message=FALSE} 
p1 <- plots_distr2K[[1]][[1]] + 
  labs(title = NULL, x = "1 year observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p2 <- plots_distr2K[[2]][[1]] + 
  labs(title = NULL, x = "3 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p3 <- plots_distr2K[[3]][[1]] + 
  labs(title = NULL, x = "3-6 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p4 <- plots_distr2K[[4]][[1]] + 
  labs(title = NULL, x = "irregular observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

distr_2K_trans1 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Coefficients density distribution for transition Dementia-free -> Dementia",  
  theme = theme(plot.title = element_text(size = 15, hjust = 0.5)))+  
  plot_layout(guides = "collect")

p1 <- plots_distr2K[[1]][[2]] + 
  labs(title = NULL, x = "1 year observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p2 <- plots_distr2K[[2]][[2]] + 
  labs(title = NULL, x = "3 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p3 <- plots_distr2K[[3]][[2]] + 
  labs(title = NULL, x = "3-6 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p4 <- plots_distr2K[[4]][[2]] + 
  labs(title = NULL, x = "irregular observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

distr_2K_trans2 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Coefficients density distribution for transition Dementia-free -> Death",  
  theme = theme(plot.title = element_text(size = 15, hjust = 0.5)))+  
  plot_layout(guides = "collect")

p1 <- plots_distr2K[[1]][[3]] + 
  labs(title = NULL, x = "1 year observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p2 <- plots_distr2K[[2]][[3]] + 
  labs(title = NULL, x = "3 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p3 <- plots_distr2K[[3]][[3]] + 
  labs(title = NULL, x = "3-6 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p4 <- plots_distr2K[[4]][[3]] + 
  labs(title = NULL, x = "irregular observation scheme") + 
  theme(axis.title.x = element_text(size = 8))
distr_2K_trans3 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Coefficients density distribution for transition Dementia -> Death",  
  theme = theme(plot.title = element_text(size = 14, hjust = 0.5)))+  
  plot_layout(guides = "collect")
  
distr_2K_trans1
distr_2K_trans2
distr_2K_trans3
```


RELATIVE BIAS OF TIME SPENT IN EACH STATE

```{r}
plfe2K
```

### Plots 5K observations

BIAS_5K
```{r}
p1 <- plots_bias5K[[1]] + labs(title= "1 year observation scheme")
p2 <- plots_bias5K[[3]] + labs(title= "3 years observation scheme")
p3 <- plots_bias5K[[5]] + labs(title= "3-6 years observation scheme")
p4 <- plots_bias5K[[7]] + labs(title= "irregular observation scheme")

plots_bias_5K <- (p1+p2) / 
                 (p3+p4) +
                 plot_layout(guides = "collect")
plots_bias_5K & 
  ylim(0, 1)
```

```{r}

p1 <- plots_bias5K[[1]]$data
p2 <- plots_bias5K[[3]]$data
p3 <- plots_bias5K[[5]]$data
p4 <- plots_bias5K[[7]]$data

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df_all <- rbind(p1,p2,p3,p4)
latex_labels <- c(
    "1" = "Transition 1",
    "2" = "Transition 2",
    "3" = "Transition 3",
    "cov1" = "beta[1]",
    "cov2" = "beta[2]",
    "cov3" = "beta[3]"
  )


 ggplot(data = df_all, aes(x = model, y = bias_mean, color = scenario)) + 
  geom_point(size = 3, shape = 19) + 
  
  facet_grid(parameter ~ transition, scales = "free", 
             labeller = labeller(parameter = as_labeller(latex_labels, label_parsed), 
                                 transition = as_labeller(latex_labels))) + 
  
  labs(title = "Bias of the estimates", 
       x = "Model", 
       y = "Bias",
       color = "Observation Scheme") + 
  
  geom_line(aes(group = scenario), size = 1, linetype = "solid", alpha = 0.8) + 
  
  #geom_errorbar(aes(ymin = bias_lower, ymax = bias_upper), width = 0.3, color = "black") + 

  theme_bw() + 
  theme(legend.position = "top", 
        axis.text.x = element_text(angle = 45, hjust = 1, size = 12), 
        plot.title = element_text(size = 14, hjust = 0.5),
        strip.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10),
        panel.spacing = unit(1, "lines"),
        axis.text.y = element_text(size = 12),
        axis.title = element_text(size = 14)) + 
  
  scale_color_viridis_d(option = "B", begin = 0.2, end = 0.8)

```

COVERAGE 5K
```{r, warning=FALSE}

p1 <- plots_cov5K[[1]] + labs(title= "1 year observation scheme")
p2 <- plots_cov5K[[2]] + labs(title= "3 years observation scheme")
p3 <- plots_cov5K[[3]] + labs(title= "3-6 years observation scheme")
p4 <- plots_cov5K[[4]] + labs(title= "irregular observation scheme")


cov_5K <- (p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect")
cov_5K
```
ERROR TYPE I 5K
```{r}
p1 <- plots_errorI5K[[1]][[1]] + labs(title = NULL,  x = "1 year observation scheme")+ theme(legend.position = "none")
p2 <- plots_errorI5K[[2]][[1]] + labs(title = NULL,  x = "3 years observation scheme") 
p3 <- plots_errorI5K[[3]][[1]] + labs(title = NULL, x = "3-6 years observation scheme")
p4 <- plots_errorI5K[[4]][[1]] + labs(title = NULL,  x = "irregular observation scheme") 

typeIerror_5K_trans1 <- (p1 + p2) / (p3 + p4) +
                  plot_layout(guides = "collect", widths = unit(rep(1, 4), "null")) +
                  plot_annotation(
                    title ="Heatmap of Type I Error by Method and Covariate for transition Dementia-free -> Dementia", 
                    theme = theme(plot.title = element_text(size = 15, hjust = 0.5)),
                  ) 
p1 <- plots_errorI5K[[1]][[2]] + labs(title = NULL,  x = "1 year observation scheme") + theme(legend.position = "none")
p2 <- plots_errorI5K[[2]][[2]] + labs(title = NULL,  x = "3 years observation scheme") 
p3 <- plots_errorI5K[[3]][[2]] + labs(title = NULL, x = "3-6 years observation scheme") 
p4 <- plots_errorI5K[[4]][[2]] + labs(title = NULL,  x = "irregular observation scheme") 

typeIerror_5K_trans3 <- (p1 + p2 )/ (p3 + p4) +
                  plot_layout(guides = "collect", widths = unit(rep(1, 4), "null")) +
                  plot_annotation(
                    title ="Heatmap of Type I Error by Method and Covariate for transition Dementia -> Death", 
                    theme = theme(plot.title = element_text(size = 15, hjust = 0.5)),
                  ) 


typeIerror_5K_trans1
typeIerror_5K_trans3

```

POWER 5K
```{r}
p1 <- plots_power5K[[1]] + labs(title =NULL, x = "1 year observation scheme")+theme(legend.position = "none")
p2 <- plots_power5K[[4]] + labs(title =NULL, x = "3 years observation scheme")
p3 <- plots_power5K[[7]] + labs(title =NULL, x = "3-6 years observation scheme")
p4 <- plots_power5K[[10]] +labs(title =NULL, x = "irregular observation scheme")

power_5K_trans1 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Heatmap of Power by Method and Covariate for transition Dementia-free -> Dementia",  
  theme = theme(plot.title = element_text(size = 15, hjust = 0.5)))+  
  plot_layout(guides = "collect")

p1 <- plots_power5K[[2]] + labs(title =NULL, x = "1 year observation scheme")
p2 <- plots_power5K[[5]] + labs(title =NULL, x = "3 years observation scheme")
p3 <- plots_power5K[[8]] + labs(title =NULL, x = "3-6 years observation scheme")
p4 <- plots_power5K[[11]] +labs(title =NULL, x = "irregular observation scheme")

power_5K_trans2 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Heatmap of Power by Method and Covariate for transition Dementia-free -> Death",  
  theme = theme(plot.title = element_text(size = 15, hjust = 0.5)))+  
  plot_layout(guides = "collect")

p1 <- plots_power5K[[3]] + labs(title =NULL, x = "1 year observation scheme")
p2 <- plots_power5K[[6]] + labs(title =NULL, x = "3 years observation scheme")
p3 <- plots_power5K[[9]] + labs(title =NULL, x = "3-6 years observation scheme")
p4 <- plots_power5K[[12]] +labs(title =NULL, x = "irregular observation scheme")

power_5K_trans3 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Heatmap of Power by Method and Covariate for transition Dementia -> Death",  
  theme = theme(plot.title = element_text(size = 15, hjust = 0.5)))+  
  plot_layout(guides = "collect")
  
power_5K_trans1
power_5K_trans2
power_5K_trans3
```

COEFFICIENTS DISTRIBUTION 5K
```{r, warning=FALSE, message=FALSE} 
p1 <- plots_distr5K[[1]][[1]] + 
  labs(title = NULL, x = "1 year observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p2 <- plots_distr5K[[2]][[1]] + 
  labs(title = NULL, x = "3 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p3 <- plots_distr5K[[3]][[1]] + 
  labs(title = NULL, x = "3-6 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p4 <- plots_distr5K[[4]][[1]] + 
  labs(title = NULL, x = "irregular observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

distr_5K_trans1 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Coefficients density distribution for transition Dementia-free -> Dementia",  
  theme = theme(plot.title = element_text(size = 15, hjust = 0.5)))+  
  plot_layout(guides = "collect")

p1 <- plots_distr5K[[1]][[2]] + 
  labs(title = NULL, x = "1 year observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p2 <- plots_distr5K[[2]][[2]] + 
  labs(title = NULL, x = "3 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p3 <- plots_distr5K[[3]][[2]] + 
  labs(title = NULL, x = "3-6 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p4 <- plots_distr5K[[4]][[2]] + 
  labs(title = NULL, x = "irregular observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

distr_5K_trans2 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Coefficients density distribution for transition Dementia-free -> Death",  
  theme = theme(plot.title = element_text(size = 15, hjust = 0.5)))+  
  plot_layout(guides = "collect")

p1 <- plots_distr5K[[1]][[3]] + 
  labs(title = NULL, x = "1 year observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p2 <- plots_distr5K[[2]][[3]] + 
  labs(title = NULL, x = "3 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p3 <- plots_distr5K[[3]][[3]] + 
  labs(title = NULL, x = "3-6 years observation scheme") + 
  theme(axis.title.x = element_text(size = 8))

p4 <- plots_distr5K[[4]][[3]] + 
  labs(title = NULL, x = "irregular observation scheme") + 
  theme(axis.title.x = element_text(size = 8))
distr_5K_trans3 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Coefficients density distribution for transition Dementia -> Death",  
  theme = theme(plot.title = element_text(size = 14, hjust = 0.5)))+  
  plot_layout(guides = "collect")
  
distr_5K_trans1
distr_5K_trans2
distr_5K_trans3
```

RELATIVE BIAS OF TIME SPENT IN EACH STATE
```{r}
plfe5K
```


### Plots 10K observations

BIAS_10K
```{r}
p1 <- plots_bias10K[[1]] + labs(title= "1 year observation scheme")
p2 <- plots_bias10K[[3]] + labs(title= "3 years observation scheme")
p3 <- plots_bias10K[[5]] + labs(title= "3-6 years observation scheme")
p4 <- plots_bias10K[[7]] + labs(title= "irregular observation scheme")

plots_bias_10K <- (p1+p2) / 
                 (p3+p4) +
                 plot_layout(guides = "collect")
plots_bias_10K & 
  ylim(0, 1)
```


```{r}

p1 <- plots_bias10K[[1]]$data
p2 <- plots_bias10K[[3]]$data
p3 <- plots_bias10K[[5]]$data
p4 <- plots_bias10K[[7]]$data

p1$scenario <- "1 year"
p2$scenario <- "3 years "
p3$scenario <- "3-6 years "
p4$scenario <- "irregular "

df_all <- rbind(p1,p2,p3,p4)
latex_labels <- c(
    "1" = "Transition 1",
    "2" = "Transition 2",
    "3" = "Transition 3",
    "cov1" = "beta[1]",
    "cov2" = "beta[2]",
    "cov3" = "beta[3]"
  )


 ggplot(data = df_all, aes(x = model, y = bias_mean, color = scenario)) + 
  geom_point(size = 3, shape = 19) + 
  
  facet_grid(parameter ~ transition, scales = "free", 
             labeller = labeller(parameter = as_labeller(latex_labels, label_parsed), 
                                 transition = as_labeller(latex_labels))) + 
  
  labs(title = "Bias of the estimates", 
       x = "Model", 
       y = "Bias",
       color = "Observation Scheme") + 
  
  geom_line(aes(group = scenario), size = 1, linetype = "solid", alpha = 0.8) + 
  
  #geom_errorbar(aes(ymin = bias_lower, ymax = bias_upper), width = 0.3, color = "black") + 

  theme_bw() + 
  theme(legend.position = "top", 
        axis.text.x = element_text(angle = 45, hjust = 1, size = 12), 
        plot.title = element_text(size = 14, hjust = 0.5),
        strip.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10),
        panel.spacing = unit(1, "lines"),
        axis.text.y = element_text(size = 12),
        axis.title = element_text(size = 14)) + 
  
  scale_color_viridis_d(option = "B", begin = 0.2, end = 0.8)

```
COVERAGE 10K
```{r, warning=FALSE}

p1 <- plots_cov10K[[1]] + labs(title= "1 year observation scheme")
p2 <- plots_cov10K[[2]] + labs(title= "3 years observation scheme")
p3 <- plots_cov10K[[3]] + labs(title= "3-6 years observation scheme")
p4 <- plots_cov10K[[4]] + labs(title= "irregular observation scheme")


cov_10K <- (p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect")
cov_10K
```

ERROR TYPE I 10K
```{r}
p1 <- plots_errorI10K[[1]][[1]] + labs(title = NULL,  x = "1 year observation scheme")+ theme(legend.position = "none")
p2 <- plots_errorI10K[[2]][[1]] + labs(title = NULL,  x = "3 years observation scheme") 
p3 <- plots_errorI10K[[3]][[1]] + labs(title = NULL, x = "3-6 years observation scheme")
p4 <- plots_errorI10K[[4]][[1]] + labs(title = NULL,  x = "irregular observation scheme") 

typeIerror_10K_trans1 <- (p1 + p2) / (p3 + p4) +
                  plot_layout(guides = "collect", widths = unit(rep(1, 4), "null")) +
                  plot_annotation(
                    title ="Heatmap of Type I Error by Method and Covariate for transition Dementia-free -> Dementia", 
                    theme = theme(plot.title = element_text(size = 15, hjust = 0.5)),
                  ) 
p1 <- plots_errorI10K[[1]][[2]] + labs(title = NULL,  x = "1 year observation scheme") + theme(legend.position = "none")
p2 <- plots_errorI10K[[2]][[2]] + labs(title = NULL,  x = "3 years observation scheme") 
p3 <- plots_errorI10K[[3]][[2]] + labs(title = NULL, x = "3-6 years observation scheme") 
p4 <- plots_errorI10K[[4]][[2]] + labs(title = NULL,  x = "irregular observation scheme") 

typeIerror_10K_trans3 <- (p1 + p2 )/ (p3 + p4) +
                  plot_layout(guides = "collect", widths = unit(rep(1, 4), "null")) +
                  plot_annotation(
                    title ="Heatmap of Type I Error by Method and Covariate for transition Dementia -> Death", 
                    theme = theme(plot.title = element_text(size = 15, hjust = 0.5)),
                  ) 


typeIerror_10K_trans1
typeIerror_10K_trans3

```


POWER 10K
```{r}
p1 <- plots_power10K[[1]] + labs(title =NULL, x = "1 year observation scheme")+theme(legend.position = "none")
p2 <- plots_power10K[[4]] + labs(title =NULL, x = "3 years observation scheme")
p3 <- plots_power10K[[7]] + labs(title =NULL, x = "3-6 years observation scheme")
p4 <- plots_power10K[[10]] +labs(title =NULL, x = "irregular observation scheme")

power_10K_trans1 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Heatmap of Power by Method and Covariate for transition Dementia-free -> Dementia",  
  theme = theme(plot.title = element_text(size = 15, hjust = 0.5)))+  
  plot_layout(guides = "collect")

p1 <- plots_power10K[[2]] + labs(title =NULL, x = "1 year observation scheme")
p2 <- plots_power10K[[5]] + labs(title =NULL, x = "3 years observation scheme")
p3 <- plots_power10K[[8]] + labs(title =NULL, x = "3-6 years observation scheme")
p4 <- plots_power10K[[11]] +labs(title =NULL, x = "irregular observation scheme")

power_10K_trans2 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Heatmap of Power by Method and Covariate for transition Dementia-free -> Death",  
  theme = theme(plot.title = element_text(size = 15, hjust = 0.5)))+  
  plot_layout(guides = "collect")

p1 <- plots_power10K[[3]] + labs(title =NULL, x = "1 year observation scheme")
p2 <- plots_power10K[[6]] + labs(title =NULL, x = "3 years observation scheme")
p3 <- plots_power10K[[9]] + labs(title =NULL, x = "3-6 years observation scheme")
p4 <- plots_power10K[[12]] +labs(title =NULL, x = "irregular observation scheme")

power_10K_trans3 <- (p1 + p2) / (p3 + p4) + 
  plot_layout(guides = "collect") + plot_annotation(
  title ="Heatmap of Power by Method and Covariate for transition Dementia -> Death",  
  theme = theme(plot.title = element_text(size = 15, hjust = 0.5)))+  
  plot_layout(guides = "collect")
  
power_10K_trans1
power_10K_trans2
power_10K_trans3
```


RELATIVE BIAS OF TIME SPENT IN EACH STATE

```{r}
plfe10K
```

### Comparing performances for different samples sizes for frequent and sporadic visits


CONVERGENCE
```{r}
t1 <- conv_table500 %>%
  select(scheme,model, `Convergence 2`) %>%
  mutate(conv500=`Convergence 2`, `Convergence 2`=NULL)
t2 <- conv_table2K %>%
  select(scheme,model, `Convergence 2`)%>%
  mutate(conv2K=`Convergence 2`, `Convergence 2`=NULL)
t3 <- conv_table5K %>%
  select(scheme,model, `Convergence 2`)%>%
  mutate(conv5K=`Convergence 2`, `Convergence 2`=NULL)
t4 <- conv_table5K %>%
  select(scheme,model, `Convergence 2`)%>%
  mutate(conv10K=`Convergence 2`, `Convergence 2`=NULL)

table_convergence <- full_join(t1,t2)
table_convergence <- full_join(table_convergence,t3)
table_convergence <- full_join(table_convergence,t4)


conv_long <- table_convergence %>%
  pivot_longer(cols = starts_with("conv"), names_to = "sample_size", values_to = "convergence") 
conv_long <- conv_long %>%
    mutate(
      sample_size = case_when(
        sample_size == "conv500" ~ "500 observations",
        sample_size == "conv2K" ~ "2K observations",
        sample_size == "conv5K" ~ "5K observations",
        sample_size == "conv10K" ~ "10K observations",
      )) %>%
  mutate(
     scheme = case_when(
        scheme == "2" ~ "1 year",
        scheme == "3" ~ "3 years",
        scheme == "4" ~ "3-6 years",
        scheme == "5" ~ "irregular",
        )) %>%
  mutate(sample_size = factor(sample_size, levels = c("500 observations", "2K observations", "5K observations", "10K observations"))) %>%
  arrange(sample_size, scheme, model)

ggplot(conv_long, aes(x = scheme, y = model, fill = convergence)) +
  geom_tile(color = "white") +
  #geom_text(aes(label = round(convergence, 1)), color = "black", size = 3) +
  facet_wrap(~sample_size) +
  scale_fill_gradient(low = "white", high = "blue", name = "Percentage (%)") +
  labs(
    title = "Heatmap of Models Convergence",
    x = "Sample Size",
    y = "Model"
  ) +
  theme_minimal()+
   theme(
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5), 
    legend.position = "top")
```



COMPUTATIONAL TIME
```{r}
t1 <- mean_ct500
t2 <- mean_ct2K
t3 <- mean_ct5K
t4 <- mean_ct10K

mean_ct_all <- rbind(t1,t2,t3,t4)
mean_ct_all$sample_size <- rep(1:4, each=4)


mean_ct_all <- mean_ct_all%>%
  pivot_longer(cols=c("a","b","c","d","e","f"),
               names_to = "model",
               values_to = "time")

ggplot(mean_ct_all, aes(x = factor(sample_size, labels = c("500", "2K", "5K", "10K")), 
                        y = time, color = model, group = model)) +
  geom_line(size = 1.2, alpha = 0.7) +
  geom_point(size = 3, alpha = 0.7)+

  facet_wrap(~ scheme, ncol = 2, scales = "fixed") + 
  scale_color_viridis_d() +
  labs(
    title = "Trend of Average Computational Time Across Sample Sizes and Observation Schemes",
    x = "Sample Size",
    y = "Time (s)",
    color = "Model"
  ) +
  theme_minimal(base_size = 14) + 
  theme(
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),  
  
    axis.title = element_text(size = 14, face = "bold"), 
    axis.text = element_text(size = 12),  
    axis.text.x = element_text(angle = 45, hjust = 1), 
    legend.position = "top", 
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    panel.grid.major = element_line(color = "gray80", size = 0.5),  
    panel.grid.minor = element_blank()  
  )


```

```{r}
disegna_scatter <- function(t, c, n, m) {

  # Verifica che tutti i vettori abbiano la stessa lunghezza
  if (!(length(t) == length(c) &&
        length(c) == length(n) &&
        length(n) == length(m))) {
    stop("Tutti i vettori devono avere la stessa lunghezza!")
  }

  # Definiamo una palette di colori in base a 'm'
  colori <- viridis(6)[as.integer(as.factor(m))]

  # Disegniamo il grafico: pch=16 (cerchi pieni),
  # cex = n (dimensione dei cerchi), col = colori
  y_low=min(c)*1.1
  y_upp=max(c)
    
  plot(
    x    = t,
    y    = c,
    pch  = 16,
    cex  = n/max(n)*3,
    col  = colori,
    xlab = "Computational Time [sec]",
    ylab = "Convergency rate [%]",
    main = "Evviva lo zio" ,  # Titolo del grafico
    ylim=c(y_low, y_upp)
  )

  # Aggiungiamo la griglia nei tick principali
  grid(nx = NULL, ny = NULL, col = "lightgray", lty = "dotted")

  # Se si vuole aggiungere una legenda, decommentare il codice seguente:
  # legend(
  #   "topright",
  #   legend = levels(factor(m)),
  #   col = rainbow(length(unique(m))),
  #   pch = 16,
  #   title = "Valori di m"
  # )
}

```

```{r}
t <- unname(unlist(c(mean_ct500[1,-1],mean_ct2K[1,-1],mean_ct5K[1,-1],mean_ct10K[1,-1])))
n <- rep(c(500,2000,5000,10000), each=6)
c <- unname(unlist(c(conv_table500[1:6,4],conv_table2K[1:6,4],conv_table5K[1:6,4],conv_table10K[1:6,4])))
m <- as.character(rep(1:6, times=4))


# t <- c(0.072990, 0.227080,  0.148680 ,  0.421870 , 0.608300  , 3.565610,  1.051761 ,  6.309565)
# n <- c(500,500,2000,2000,5000,5000,10000,10000)
# c <- c(82,100,83,100, 87,100,77,100)
# m <- as.character(rep(1:2, times=4))
# 
disegna_scatter(t,c,n,m)

```





BIAS COMPARISON (1 Year)
```{r}
p1 <- plots_bias500[[1]] + 
  labs(title =NULL, caption = "500 observations") +
  geom_point(size=0.5)
p2 <- plots_bias2K[[1]] + 
  labs(title= NULL, caption = "2K observations") +
  geom_point(size=0.5)
p3 <- plots_bias5K[[1]] + 
  labs(title= NULL, caption = "5K observations") +
  geom_point(size=0.5)
p4 <- plots_bias10K[[1]] + 
  labs(title= NULL, caption = "10K observations") +
  geom_point(size=0.5)


plots_bias_all <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Bias comparison (1 year)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

plots_bias_all & 
  ylim(0, 1.5)
```


BIAS COMPARISON (3-6 years)
```{r}
p1 <- plots_bias500[[5]] + 
  labs(title =NULL, caption = "500 observations") +
  geom_point(size=0.5)
p2 <- plots_bias2K[[5]] + 
  labs(title= NULL, caption = "2K observations") +
  geom_point(size=0.5)
p3 <- plots_bias5K[[5]] + 
  labs(title= NULL, caption = "5K observations") +
  geom_point(size=0.5)
p4 <- plots_bias10K[[5]] + 
  labs(title= NULL, caption = "10K observations") +
  geom_point(size=0.5)


plots_bias_all <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Bias comparison (3-6 years)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

plots_bias_all & 
  ylim(0, 3)
```
```{r}

df_scenario <- function(scenario,title){
  p1 <- plots_bias500[[scenario]]$data
  p2 <- plots_bias2K[[scenario]]$data
  p3 <- plots_bias5K[[scenario]]$data
  p4 <- plots_bias10K[[scenario]]$data
  
  
  p1$size <- "500 observations"
  p2$size <- "2K observations"
  p3$size <- "5K observations"
  p4$size <- "10K observations"
  
  df_all <- rbind(p1,p2,p3,p4)
  df_all$size <- factor(df_all$size, levels = c("500 observations", "2K observations", "5K observations", "10K observations"))
  df_all <- df_all[order(df_all$size), ]
  df_all$scenario <- title
  return(df_all)
}

df_all1 <- df_scenario(1,"1 year")
df_all2 <- df_scenario(3,"3 years")
df_all3 <- df_scenario(5,"3-6 years")
df_all4 <- df_scenario(7,"irregular")

create_plot <- function(df){
  latex_labels <- c(
    "1" = "Transition 1",
    "2" = "Transition 2",
    "3" = "Transition 3",
    "cov1" = "beta[1]",
    "cov2" = "beta[2]",
    "cov3" = "beta[3]"
  )
  ggplot(data = df, aes(x = model, y = bias_mean, color = size)) + 
  geom_point(size = 3, shape = 19) + 
  
  facet_grid(parameter ~ transition, scales = "free", 
             labeller = labeller(parameter = as_labeller(latex_labels, label_parsed), 
                                 transition = as_labeller(latex_labels)),) + 
  
  labs(title = NULL, 
       x = NULL, 
       y = NULL) + 
  
  geom_line(aes(group = size), size = 1, linetype = "solid", alpha = 0.8) + 
  theme_bw() + 
  theme(legend.position = "top", 
        axis.text.x = element_text(angle = 45, hjust = 1, size = 12), 
        plot.title = element_text(size = 14, hjust = 0.5),
        strip.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10),
        panel.spacing = unit(1, "lines"),
        axis.text.y = element_text(size = 12),
        axis.title = element_text(size = 14)) + 
  
  scale_color_viridis_d(option = "C", begin = 0.2, end = 0.8)
  
}

plot1 <- create_plot(df_all1)+labs(caption = "1 year observation scheme")
plot2 <- create_plot(df_all2)+labs(caption = "3 years observation scheme")
plot3 <- create_plot(df_all3)+labs(caption = "3-6 years observation scheme")
plot4 <- create_plot(df_all4)+labs(caption = "irregular observation scheme")

 ( plot1+plot2) / (plot3+plot4) + plot_layout(guides = "collect")+
  plot_annotation(title = "Bias of Estimates")& 
  theme(legend.position = "top", 
        legend.title = element_text(size = 12), 
        legend.text = element_text(size = 10), 
        plot.title = element_text(size = 14, hjust = 0.5)) 
 # ylim(0,3)
  

```


COVERAGE COMPARISON (1 year)
```{r, warning=FALSE}
p1 <- plots_cov500[[1]] + 
  labs(title =NULL, caption = "500 observations") +
  geom_point(size=0.5)
p2 <- plots_cov2K[[1]] + 
  labs(title= NULL, caption = "2K observations") +
  geom_point(size=0.5)
p3 <- plots_cov5K[[1]] + 
  labs(title= NULL, caption = "5K observations") +
  geom_point(size=0.5)
p4 <- plots_cov10K[[1]] + 
  labs(title= NULL, caption = "10K observations") +
  geom_point(size=0.5)

plots_cov_all <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Coverage comparison (1 year)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

plots_cov_all & 
  ylim(0, 1)
```


COVERAGE COMPARISON (3-6 years)
```{r, warning=FALSE}
p1 <- plots_cov500[[3]] + 
  labs(title =NULL, caption = "500 observations") +
  geom_point(size=0.5)
p2 <- plots_cov2K[[3]] + 
  labs(title= NULL, caption = "2K observations") +
  geom_point(size=0.5)
p3 <- plots_cov5K[[3]] + 
  labs(title= NULL, caption = "5K observations") +
  geom_point(size=0.5)
p4 <- plots_cov10K[[3]] + 
  labs(title= NULL, caption = "10K observations") +
  geom_point(size=0.5)

plots_cov_all <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Coverage comparison (3-6 years)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

plots_cov_all & 
  ylim(0, 1)
```


ERROR TYPE I COMPARISON (1 year)
```{r, warning=FALSE}
p1 <- plots_errorI500[[1]][[1]] + 
  labs(title =NULL, x=NULL, caption = "500 observations") +
  geom_point(size=0.5) 
p2 <- plots_errorI2K[[1]][[1]] + 
  labs(title= NULL, x=NULL, caption = "2K observations") +
  geom_point(size=0.5)
p3 <- plots_errorI5K[[1]][[1]] + 
  labs(title= NULL, x=NULL, caption = "5K observations") +
  geom_point(size=0.5)
p4 <- plots_errorI5K[[1]][[1]] + 
  labs(title= NULL, x=NULL, caption = "10K observations") +
  geom_point(size=0.5)

plots_errorI_all_trans1 <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Type I error comparison on transition Dementia-free -> Dementia (3-6 years)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

p1 <- plots_errorI500[[1]][[2]] + 
  labs(title =NULL, x=NULL, caption = "500 observations") +
  geom_point(size=0.5)+ theme(legend.position = "none")
p2 <- plots_errorI2K[[1]][[2]] + 
  labs(title= NULL, x=NULL, caption = "2K observations") +
  geom_point(size=0.5)
p3 <- plots_errorI5K[[1]][[2]] + 
  labs(title= NULL, x=NULL, caption = "5K observations") +
  geom_point(size=0.5)+ theme(legend.position = "none")
p4 <- plots_errorI5K[[1]][[2]] + 
  labs(title= NULL, x=NULL, caption = "10K observations") +
  geom_point(size=0.5)+ theme(legend.position = "none")

plots_errorI_all_trans3 <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Type I error comparison on transition Dementia-> Death (1 year)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

plots_errorI_all_trans1
plots_errorI_all_trans3
```


ERROR TYPE I COMPARISON (3-6)
```{r, warning=FALSE}
p1 <- plots_errorI500[[3]][[1]] + 
  labs(title =NULL, x=NULL, caption = "500 observations") +
  geom_point(size=0.5) 
p2 <- plots_errorI2K[[3]][[1]] + 
  labs(title= NULL, x=NULL, caption = "2K observations") +
  geom_point(size=0.5)
p3 <- plots_errorI5K[[3]][[1]] + 
  labs(title= NULL, x=NULL, caption = "5K observations") +
  geom_point(size=0.5)
p4 <- plots_errorI5K[[3]][[1]] + 
  labs(title= NULL, x=NULL, caption = "10K observations") +
  geom_point(size=0.5)

plots_errorI_all_trans1 <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Type I error comparison on transition Dementia-free -> Dementia (3-6 years)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

p1 <- plots_errorI500[[3]][[2]] + 
  labs(title =NULL, x=NULL, caption = "500 observations") +
  geom_point(size=0.5) 
p2 <- plots_errorI2K[[3]][[2]] + 
  labs(title= NULL, x=NULL, caption = "2K observations") +
  geom_point(size=0.5)+ theme(legend.position = "none")
p3 <- plots_errorI5K[[3]][[2]] + 
  labs(title= NULL, x=NULL, caption = "5K observations") +
  geom_point(size=0.5)+ theme(legend.position = "none")
p4 <- plots_errorI5K[[3]][[2]] + 
  labs(title= NULL, x=NULL, caption = "10K observations") +
  geom_point(size=0.5)+ theme(legend.position = "none")

plots_errorI_all_trans3 <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Type I error comparison on transition Dementia-> Death (3-6 years)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

plots_errorI_all_trans1
plots_errorI_all_trans3
```


POWER COMPARISON (1 year) 
```{r warning=FALSE}
p1 <- plots_power500[[1]] + 
  labs(title =NULL, x=NULL, caption = "500 observations") +
  geom_point(size=0.5)+ theme(legend.position = "none")
p2 <- plots_power2K[[1]] + 
  labs(title= NULL, x=NULL, caption = "2K observations") +
  geom_point(size=0.5)
p3 <- plots_power5K[[1]] + 
  labs(title= NULL, x=NULL, caption = "5K observations") +
  geom_point(size=0.5)+theme(legend.position = "none")
p4 <- plots_power5K[[1]] + 
  labs(title= NULL, x=NULL, caption = "10K observations") +
  geom_point(size=0.5)+theme(legend.position = "none")

plots_power_all_trans1 <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Power comparison on transition Dementia-free -> Dementia (1 year)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

p1 <- plots_power500[[2]] + 
  labs(title =NULL, x=NULL, caption = "500 observations") +
  geom_point(size=0.5)
p2 <- plots_power2K[[2]] + 
  labs(title= NULL, x=NULL, caption = "2K observations") +
  geom_point(size=0.5)+ theme(legend.position = "none")
p3 <- plots_power5K[[2]] + 
  labs(title= NULL, x=NULL, caption = "5K observations") +
  geom_point(size=0.5)
p4 <- plots_power5K[[2]] + 
  labs(title= NULL, x=NULL, caption = "10K observations") +
  geom_point(size=0.5)

plots_power_all_trans2 <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Power comparison on transition Dementia-free-> Death (1 year)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

p1 <- plots_power500[[3]] + 
  labs(title =NULL, x=NULL, caption = "500 observations") +
  geom_point(size=0.5)+ theme(legend.position = "none")
p2 <- plots_power2K[[3]] + 
  labs(title= NULL, x=NULL, caption = "2K observations") + theme(legend.position = "none")
  geom_point(size=0.5)
p3 <- plots_power5K[[3]] + 
  labs(title= NULL, x=NULL, caption = "5K observations") +
  geom_point(size=0.5)
p4 <- plots_power5K[[3]] + 
  labs(title= NULL, x=NULL, caption = "10K observations") +
  geom_point(size=0.5)

plots_power_all_trans3 <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Power comparison on transition Dementia-> Death (1 year)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

plots_power_all_trans1
plots_power_all_trans2
plots_power_all_trans3
```


POWER COMPARISON (3-6 years)
```{r warning=FALSE}
p1 <- plots_power500[[7]] + 
  labs(title =NULL, x=NULL, caption = "500 observations") +
  geom_point(size=0.5)+ theme(legend.position = "none")
p2 <- plots_power2K[[7]] + 
  labs(title= NULL, x=NULL, caption = "2K observations") +
  geom_point(size=0.5)
p3 <- plots_power5K[[7]] + 
  labs(title= NULL, x=NULL, caption = "5K observations") +
  geom_point(size=0.5)
p4 <- plots_power5K[[7]] + 
  labs(title= NULL, x=NULL, caption = "10K observations") +
  geom_point(size=0.5)

plots_power_all_trans1 <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Power comparison on transition Dementia-free -> Dementia (3-6 years)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

p1 <- plots_power500[[8]] + 
  labs(title =NULL, x=NULL, caption = "500 observations") +
  geom_point(size=0.5)
p2 <- plots_power2K[[8]] + 
  labs(title= NULL, x=NULL, caption = "2K observations") +
  geom_point(size=0.5)+ theme(legend.position = "none")
p3 <- plots_power5K[[8]] + 
  labs(title= NULL, x=NULL, caption = "5K observations") +
  geom_point(size=0.5)
p4 <- plots_power5K[[8]] + 
  labs(title= NULL, x=NULL, caption = "10K observations") +
  geom_point(size=0.5)

plots_power_all_trans2 <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Power comparison on transition Dementia-free-> Death (3-6 years)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

p1 <- plots_power500[[9]] + 
  labs(title =NULL, x=NULL, caption = "500 observations") +
  geom_point(size=0.5)+ theme(legend.position = "none")
p2 <- plots_power2K[[9]] + 
  labs(title= NULL, x=NULL, caption = "2K observations") + theme(legend.position = "none")
  geom_point(size=0.5)
p3 <- plots_power5K[[9]] + 
  labs(title= NULL, x=NULL, caption = "5K observations") +
  geom_point(size=0.5)
p4 <- plots_power5K[[9]] + 
  labs(title= NULL, x=NULL, caption = "10K observations") +
  geom_point(size=0.5)

plots_power_all_trans3 <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Power comparison on transition Dementia-> Death (3-6 years)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

plots_power_all_trans1
plots_power_all_trans2
plots_power_all_trans3
```


COEFFICIENT DISTRIBUTION (1 year)
```{r warning=FALSE, message=FALSE}
p1 <- plots_distr500[[1]][[1]] + 
  labs(title =NULL, x=NULL, caption = "500 observations") 
p2 <- plots_distr2K[[1]][[1]] + 
  labs(title= NULL, x=NULL, caption = "2K observations") 
p3 <- plots_distr5K[[1]][[1]] + 
  labs(title= NULL, x=NULL, caption = "5K observations") 
p4 <- plots_distr10K[[1]][[1]] + 
  labs(title= NULL, x=NULL, caption = "10K observations") 

plots_distr_all_trans1 <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Coefficients distribution comparison on transition Dementia-free -> Dementia (1 year)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

p1 <- plots_distr500[[1]][[2]] + 
  labs(title =NULL, x=NULL, caption = "500 observations") 
p2 <- plots_distr2K[[1]][[2]] + 
  labs(title= NULL, x=NULL, caption = "2K observations") 
p3 <- plots_distr5K[[1]][[2]] + 
  labs(title= NULL, x=NULL, caption = "5K observations") 
p4 <- plots_distr10K[[1]][[2]] + 
  labs(title= NULL, x=NULL, caption = "10K observations") 

plots_distr_all_trans2 <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Coefficients distribution comparison on transition Dementia-free-> Death (1 year)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

p1 <- plots_distr500[[1]][[3]] + 
  labs(title =NULL, x=NULL, caption = "500 observations") 
p2 <- plots_distr2K[[1]][[3]] + 
  labs(title= NULL, x=NULL, caption = "2K observations") 
p3 <- plots_distr5K[[1]][[3]] + 
  labs(title= NULL, x=NULL, caption = "5K observations") 
p4 <- plots_distr10K[[1]][[3]] + 
  labs(title= NULL, x=NULL, caption = "10K observations") 

plots_distr_all_trans3 <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Coefficients distribution comparison on transition Dementia-> Death (1 year)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

plots_distr_all_trans1
plots_distr_all_trans2
plots_distr_all_trans3
```


COEFFICIENT DISTRIBUTION (3-6 years)
```{r warning=FALSE, message=FALSE}
p1 <- plots_distr500[[3]][[1]] + 
  labs(title =NULL, x=NULL, caption = "500 observations") 
p2 <- plots_distr2K[[3]][[1]] + 
  labs(title= NULL, x=NULL, caption = "2K observations") 
p3 <- plots_distr5K[[3]][[1]] + 
  labs(title= NULL, x=NULL, caption = "5K observations") 
p4 <- plots_distr10K[[3]][[1]] + 
  labs(title= NULL, x=NULL, caption = "10K observations") 

plots_distr_all_trans1 <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Coefficients distribution comparison on transition Dementia-free -> Dementia (3-6 years)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

p1 <- plots_distr500[[3]][[2]] + 
  labs(title =NULL, x=NULL, caption = "500 observations") 
p2 <- plots_distr2K[[3]][[2]] + 
  labs(title= NULL, x=NULL, caption = "2K observations") 
p3 <- plots_distr5K[[3]][[2]] + 
  labs(title= NULL, x=NULL, caption = "5K observations") 
p4 <- plots_distr10K[[3]][[2]] + 
  labs(title= NULL, x=NULL, caption = "10K observations") 

plots_distr_all_trans2 <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Coefficients distribution comparison on transition Dementia-free-> Death (3-6 years)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

p1 <- plots_distr500[[3]][[3]] + 
  labs(title =NULL, x=NULL, caption = "500 observations") 
p2 <- plots_distr2K[[3]][[3]] + 
  labs(title= NULL, x=NULL, caption = "2K observations") 
p3 <- plots_distr5K[[3]][[3]] + 
  labs(title= NULL, x=NULL, caption = "5K observations") 
p4 <- plots_distr10K[[3]][[3]] + 
  labs(title= NULL, x=NULL, caption = "10K observations") 

plots_distr_all_trans3 <- ( p1+p2) / (p3+p4) +
                 plot_layout(guides = "collect") + 
  plot_annotation(title = "Coefficients distribution comparison on transition Dementia-> Death (3-6 years)",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)))

plots_distr_all_trans1
plots_distr_all_trans2
plots_distr_all_trans3
```


RELATIVE BIAS OF TIME SPENT IN EACH STATE (3-6 years)
```{r}
df_subset500 <- plfe500$data[plfe500$data$scenario == "3-6 years observation scheme", ]
df_subset2K <- plfe2K$data[plfe2K$data$scenario == "3-6 years observation scheme", ]
df_subset5K <- plfe5K$data[plfe5K$data$scenario == "3-6 years observation scheme", ]
df_subset10K <- plfe10K$data[plfe10K$data$scenario == "3-6 years observation scheme", ]

 df_all <- rbind(
      transform(df_subset500, size = "500 observations"),
      transform(df_subset2K, size = "2K observations"),
      transform(df_subset5K, size = "5K observations"),
      transform(df_subset10K, size = "10K observations")
    )
 df_all$size <- factor(df_all$size, levels = c("500 observations", "2K observations", "5K observations", "10K observations"))
df_all <- df_all[order(df_all$size), ]

  ggplot(df_all, aes(x = model, y = lfe_mean, fill = as.factor(dem))) +
      geom_bar(stat = "identity", position = position_dodge(width = 0.7), width = 0.4) +
      geom_errorbar(aes(ymin = lfe_lower_ci, ymax = lfe_upper_ci),
                    position = position_dodge(width = 0.7), width = 0.25) +
      labs(
        title = "Relative Bias of Time Spent in State",
        x = NULL,
        y = "Relative Bias (%)",
        fill = NULL
      ) +
      scale_y_continuous(limits = c(-1, 0.7)) +
      scale_fill_manual(values = c("0" = "skyblue", "1" = "purple"),
                        labels = c("Dementia-free", "Dementia")) +
      theme_minimal() +
      theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 12, hjust = 0.5),
        legend.position = "top", 
        legend.margin = margin(t = 10),  
        panel.spacing = unit(1, "lines") 
      ) +
      facet_wrap(~size, ncol = 2)
    
```

